\part{2010}
\renewcommand\resultsyear{2010}


\chapter{Referendums in 2010}

\section{Tower Hamlets Mayoral Referendum}
\index{Tower Hamlets!Mayoral Referendum}

One referendum was held in 2010, on 6 May 2010 in the London Borough of Tower Hamlets on the question of whether the borough should have a directly elected Mayor:\label{thref:20100506}

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
& Yes & 60758\\
& No & 39857\\
\end{tabular*}

%\part{By-elections}

\chapter{Parliamentary by-elections}

There were no parliamentary by-elections in 2010.

At the dissolution of Parliament in advance of the 6th May 2010 general election three seats were vacant: Middlesbrough South and East Cleveland (caused by the death of Ashok Kumar, Lab), North West Leicestershire (caused by the death of David Taylor, Lab), and Strangford (caused by the resignation of Iris Robinson, DUP).
\index{Middlesbrough South and East Cleveland , House of Commons@Middlesbrough S. \& East Cleveland, \emph{House of Commons}}
\index{North West Leicestershire , House of Commons@North West Leics., \emph{House of Commons}}
\index{Strangford , House of Commons@Strangford, \emph{House of Commons}}

The general election in the Thirsk and Malton constituency was postponed to 27th May 2010 following the death of the originally nominated UKIP candidate, John Boakes:

\section*{Thirsk and Malton}\label{ThirskMalton}

\index{Thirsk and Malton , House of Commons@Thirsk \& Malton, \emph{House of Commons}}

 \begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
McIntosh, A. Ms.*&C&20167\\
Keal, H.&LD&8886\\
Roberts, J.&Lab&5169\\
Horton, T.&UKIP&2502\\
Clark, J.S.&Lib&1418\\ \end{tabular*}\par


\chapter{By-elections to devolved assemblies and the European Parliament}

\section{Greater London Authority}

There were no by-elections in 2010 to the Greater London Authority.

\section{National Assembly for Wales}

There were no by-elections in 2010 to the National Assembly for Wales.

\section{Scottish Parliament}

There were no by-elections in 2010 to the Scottish Parliament.

\section{Northern Ireland Assembly}

Vacancies in the Northern Ireland Assembly are filled by co-option.  The following members were co-opted to the Assembly in 2010:
\begin{itemize}
\item Billy Leonard (SF) was co-opted on 7th January following the resignation of Francie Brolly (East Londonderry).
\item Jonathan Bell (DUP) was co-opted on 22nd January following the resignation of Iris Robinson (Strangford).
\item Conal McDevitt (SDLP) was co-opted on 21st May following the resignation of Carmel Hanna (Belfast South).
\item Paul Givan (DUP) was co-opted on 10th June following the resignation of Jeffrey Donaldson (Lagan Valley).
\item Paul Frew (DUP) was co-opted on 21st June following the resignation of Ian Paisley Jr (Antrim North).
\item Sydney Anderson and Paul Girvan (both DUP) were co-opted on 1st July following the resignations of David Simpson (Upper Bann) and William McCrea (Antrim South) respectively.
\item Chris Lyttle (APNI) was co-opted on 5th July following the resignation of Naomi Long (Belfast East).
\item Simpson Gibson (DUP) was co-opted on 2nd August following the resignation of Jim Shannon (Strangford).
\item William Humphrey (DUP) was co-opted on 13th September following the resignation of Nigel Dodds (Belfast North).
\item P\'ol Callaghan (SDLP) was co-opted on 15th November following the resignation of Mark Durkan (Foyle).
\item Pat Sheehan (SF) was co-opted on 7th December following the resignation of Gerry Adams (Belfast West).
\end{itemize}

\section{European Parliament}

UK vacancies in the European Parliament are filled by the next available person from the party list at the most recent election (which was held in 2009).  The following replacement was made in 2010:
\begin{itemize}
\item Keith Taylor (Grn) replaced Caroline Lucas following her resignation on 17th May (South East).
\end{itemize}

\chapter{Local by-elections and unfilled vacancies}

\begin{resultsiii}

\section{North London}

\subsection{City of London Corporation}
\index{City of London}

\subsubsection*{Bassishaw \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[Wednesday 21st April]}

\index{Bassishaw , City of London@Bassishaw, \emph{City of London}}

Aldermanic election: retirement of Sir David Brewer (Ind).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Philip Remnant & Ind & 130\\
Mark Watson-Gandy & Ind & 31\\
\end{tabular*}

\subsubsection*{Queenhithe \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[Tuesday 5th October]}

\index{Queenhithe , City of London@Queenhithe, \emph{City of London}}

Aldermanic election: Gordon Haines (Ind) sought re-election.

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Gordon Haines & Ind & \emph{unop.}\\
\end{tabular*}

\subsection{Barking and Dagenham}
\index{Barking and Dagenham}

\subsubsection*{Goresbrook \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[8th July]}

\index{Goresbrook , Barking and Dagenham@Goresbrook, \emph{Barking \& Dagenham}}

Disqualification (employed by the council, lollipop lady) of Louise Couling (Lab).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Louise Couling & Lab & 881\\
Richard Barnbrook & BNP & 642\\
Felicia Taiwo & LD & 136\\
Paul Ayer & C & 108\\
Warren Northover & Ind & 63\\
Nobby Manning & UKIP & 50\\
Faruk Choudhury & Ind & 11\\
\end{tabular*}

\subsection{Barnet}
\index{Barnet}

At the May 2010 ordinary election there was an unfilled vacancy in Golders Green ward due to the resignation of Chris Harris (C).
\index{Golders Green , Barnet@Golders Green, \emph{Barnet}}

\subsection{Camden}
\index{Camden}

\subsubsection*{Haverstock (3) \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[Tuesday 25th May; 2 LD gains from Lab]}%\label{CamdenHaverstock}

\index{Haverstock , Camden@Haverstock, \emph{Camden}}

Ordinary election postponed from 6th May; death of outgoing councillor Syed Hoque (LD elected as Labour) who had been nominated for re-election.

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Jill Fraser & LD & 1462\\
Matt Sanders & LD & 1326\\
Rahel Bokth & LD & 1291\\
Sabrina Francis & Lab & 1257\\
Tom Copley & Lab & 1202\\
Joynal Uddin & Lab & 1114\\
Joan Stally & C & 259\\
Tom Frost & C & 250\\
Jane Lawrie & Grn & 246\\
Paul Grader & Grn & 240\\
Robert Ricketts & C & 236\\
Sean Thompson & Grn & 181\\
\end{tabular*}

\subsubsection*{Frognal and Fitzjohns \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[22nd July]}

\index{Frognal and Fitzjohns , Camden@Frognal \& Fitzjohns, \emph{Camden}}

Death of Martin Davies (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Gio Spinella & C & 1061\\
David Bouchier & LD & 329\\
Jack Smith & Lab & 235\\
Charles Harris & Grn & 71\\
\end{tabular*}

\subsubsection*{Kentish Town \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[28th October]}

\index{Kentish Town , Camden@Kentish Town, \emph{Camden}}

Death of Dave Horan (Lab).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Jenny Headlam-Wells & Lab & 1411\\
Nick Russell & LD & 715\\
Naomi Aptowitzer & Grn & 349\\
Will Blair & C & 186\\
\end{tabular*}

\subsection{Hackney}
\index{Hackney}

\subsubsection*{New River \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[16th September]}

\index{New River , Hackney@New River, \emph{Hackney}}

Death of Maureen Middleton (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Benzion Papier & C & 1567\\
Jonathan Burke & Lab & 1007\\
Stuart Coggins & Grn & 77\\
Benjamin Mathis & LD & 61\\
Darren Fraser & Ind & 26\\
\end{tabular*}

\subsection{Hammersmith and Fulham}
\index{Hammersmith and Fulham}

At the May 2010 ordinary election there was an unfilled vacancy in Avonmore and Brook Green ward due to the resignation of Will Bethell (C).
\index{Avonmore and Brook Green , Hammersmith and Fulham@Avonmore \& Brook Green, \emph{Hammersmith \& Fulham}}

\subsection{Havering}
\index{Havering}

At the May 2010 ordinary election there was an unfilled vacancy in Elm Park ward due to the resignation of David Grantham (C).
\index{Elm Park , Havering@Elm Park, \emph{Havering}}

\subsection{Islington}
\index{Islington}

At the May 2010 ordinary election there was an unfilled vacancy in Bunhill ward due to the death of Donna Boffa (LD).
\index{Bunhill , Islington@Bunhill, \emph{Islington}}

\subsection{Kensington and Chelsea}
\index{Kensington and Chelsea}

\subsubsection*{Holland \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[22nd July]}

\index{Holland , Kensington and Chelsea@Holland, \emph{Kensington \& Chelsea}}

Resignation of Baroness Hanham (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Rock Feilding-Mellen & C & 649\\
Martin Wilson & LD & 146\\
Jack Bovill & Ind & 70\\
\end{tabular*}

\subsubsection*{Cremorne \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[16th September]}

\index{Cremorne , Kensington and Chelsea@Cremorne, \emph{Kensington \& Chelsea}}

Resignation of Mark Daley (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Gerard Hargreaves & C & 602\\
Mabel McKeown & Lab & 583\\
Peter Kosta & LD & 180\\
Julia Stephenson & Grn & 51\\
David Coburn & UKIP & 46\\
\end{tabular*}

\subsubsection*{Earl's Court \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[16th September; LD gain from C]}

\index{Earl's Court , Kensington and Chelsea@Earl's Court, \emph{Kensington \& Chelsea}}

Resignation of Barry Phelps (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Linda Wade & LD & 703\\
Malcolm Spalding & C & 594\\
Joel Bishop & Lab & 151\\
Elizabeth Arbuthnot & Ind & 49\\
Jack Bovill & Ind & 29\\
Michael Enright & Grn & 26\\
Antony Little & UKIP & 18\\
\end{tabular*}

\subsection{Redbridge}
\index{Redbridge}

\subsubsection*{Chadwell \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[8th July]}

\index{Chadwell , Redbridge@Chadwell, \emph{Redbridge}}

Disqualification (employed by the council, schoolteacher) of Mark Gittens (Lab).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Wes Streeting & Lab & 800\\
Gary Monro & C & 580\\
John Tyne & LD & 576\\
Wilson Chowdhry & Grn & 413\\
Julian Leppert & BNP & 115\\
Paul Wiffen & UKIP & 54\\
\end{tabular*}

\subsection{Tower Hamlets}
\index{Tower Hamlets}

\subsubsection*{Spitalfields and Banglatown \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[16th December; Respect gain from Lab]}

\index{Spitalfields and Banglatown , Tower Hamlets@Spitalfields \& Banglatown, \emph{Tower Hamlets}}

Election of Lutfur Rahman (Ind elected as Lab) as Mayor of Tower Hamlets.

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Fozol Miah & Respect & 666\\
Abdul Alim & Lab & 553\\
Matthew Smith & C & 135\\
Margaret Crosbie & Grn & 52\\
Fernando North & LD & 33\\
Jewel Choudhury & Ind & 28\\
\end{tabular*}

\subsection{Westminster}
\index{Westminster}

At the May 2010 ordinary election there was an unfilled vacancy in Bryanston and Dorset Square ward due to the death of Angela Hooper (C).
\index{Bryanston and Dorset Square , Westminster@Bryanston \& Dorset Square, \emph{Westminster}}

\section{South London}

\subsection{Bexley}
\index{Bexley}

At the May 2010 ordinary election there was an unfilled vacancy in Barnehurst ward due to the disqualification (non-attendance) of Bill McEwen (C).
\index{Barnehurst , Bexley@Barnehurst, \emph{Bexley}}

\subsection{Bromley}
\index{Bromley}

At the May 2010 ordinary election there was an unfilled vacancy in Bromley Town ward due to the resignation of Stephen Maly (C).
\index{Bromley Town , Bromley@Bromley Town, \emph{Bromley}}

\subsection{Croydon}
\index{Croydon}

At the May 2010 ordinary election there was an unfilled vacancy in Ashburton ward due to the death of Lindsay Frost (C).
\index{Ashburton , Croydon@Ashburton, \emph{Croydon}}

\subsection{Greenwich}
\index{Greenwich}

At the May 2010 ordinary election there was an unfilled vacancy in Eltham South ward due to the resignation of Elizabeth Truss (C).
\index{Eltham South , Greenwich@Eltham S., \emph{Greenwich}}

\subsection{Lambeth}
\index{Lambeth}

\subsubsection*{Tulse Hill \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[1st July]}

\index{Tulse Hill , Lambeth@Tulse Hill, \emph{Lambeth}}

Resignation of Toren Smith (Lab).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Ruth Ling & Lab & 1235\\
Terence Curtis & LD & 745\\
George Graham & Grn & 256\\
Alan Blackburn & C & 94\\
Robin Lambert & UKIP & 36\\
\end{tabular*}

\subsection{Lewisham}
\index{Lewisham}

At the May 2010 ordinary election there was an unfilled vacancy in Whitefoot ward due to the resignation of Cathy Priddey (LD).
\index{Whitefoot , Lewisham@Whitefoot, \emph{Lewisham}}

LPBP = Lewisham People Before Profit

\subsubsection*{Ladywell \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[4th November]}

\index{Ladywell , Lewisham@Ladywell, \emph{Lewisham}}

Resignation of Tim Shand (Lab).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Carl Handley & Lab & 1231\\
Ute Michel & Grn & 1041\\
Ingrid Chetram & LD & 314 \\
Helen Mercer & LPBP & 233\\
Benjamin Appleby & C & 153\\
\end{tabular*}

\subsection{Southwark}
\index{Southwark}

At the May 2010 ordinary election there was an unfilled vacancy in The Lane ward due to the resignation of Susan Elan Jones (Lab).
\index{Lane , Southwark@The Lane, \emph{Southwark}}

\subsection{Wandsworth}
\index{Wandsworth}

At the May 2010 ordinary election there was an unfilled vacancy in East Putney ward due to the death of Prof Brian Prichard (C).
\index{East Putney , Wandsworth@East Putney, \emph{Wandsworth}}

\section{Greater Manchester}

\subsection{Bury}
\index{Bury}

\subsubsection*{Pilkington Park \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Pilkington Park , Bury@Pilkington Park, \emph{Bury}}

Resignation of Peter Redstone (C).

This by-election was combined with the 2010 ordinary election.
%; see page \pageref{PilkingtonParkBury} for the result.

\subsection{Manchester}
\index{Manchester}

\subsubsection*{Hulme \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[4th November]}

\index{Hulme , Manchester@Hulme, \emph{Manchester}}

Resignation of Emily Lomax (Lab).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Amina Lone & Lab & 1031\\
Deyika Nzeribe & Grn & 451\\
Grace Baynham & LD & 151\\
Will Stobart & C & 67\\
\end{tabular*}

%\subsubsection*{Baguley \hspace*{\fill}\nolinebreak[1]%
%\enspace\hspace*{\fill}
%\finalhyphendemerits=0
%[tba]}
%
%\index{Baguley , Manchester@Baguley, Manchester}
%
%Death of Eddie McCulley (Lab).
%
%\noindent
%\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
%.
%\end{tabular*}

\subsection{Rochdale}
\index{Rochdale}

\subsubsection*{Healey \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Healey , Rochdale@Healey, \emph{Rochdale}}

Resignation of Elwyn Watkins (LD).

This by-election was combined with the 2010 ordinary election.
%; see page \pageref{HealeyRochdale} for the result.

\subsection{Tameside}
\index{Tameside}

\subsubsection*{Longdendale \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[30th September]}

\index{Longdendale , Tameside@Longdendale, \emph{Tameside}}

Death of Roy Oldham (Lab).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Janet Cooper & Lab & 1275\\
Rob Adlard & C & 1083\\
Melanie Roberts & Grn & 99\\
Anthony Jones & BNP & 80\\
Kevin Misell & UKIP & 67\\
\end{tabular*}

\subsection{Trafford}
\index{Trafford}

\subsubsection*{Bowdon \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Bowdon , Trafford@Bowdon, \emph{Trafford}}

Resignation of Stephanie Poole (C).

This by-election was combined with the 2010 ordinary election.
%; see page \pageref{BowdonTrafford} for the result.

\section{Merseyside}

\subsection{Knowsley}
\index{Knowsley}

\subsubsection*{St Gabriels \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Saint Gabriels , Knowsley@St Gabriels, \emph{Knowsley}}

Resignation of Mike Currie (LD).

This by-election was originally scheduled for 25th March but was postponed following the death of the Labour candidate Mike Peers.  It was then combined with the 2010 ordinary election.
%; see page \pageref{StGabrielsKnowsley} for the result.

\subsubsection*{Park \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[16th September]}

\index{Park , Knowsley@Park, \emph{Knowsley}}

Resignation of Margaret Dobbie (Lab).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Tony Brennan & Lab & 650\\
John White & LD & 70\\
Gary Robertson & C & 36\\
\end{tabular*}

\subsection{Liverpool}
\index{Liverpool}

EDP = English Democrats Party

\subsubsection*{Fazakerley \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[18th February]}

\index{Fazakerley , Liverpool@Fazakerley, \emph{Liverpool}}

Death of Jack Spriggs (Lab).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Louise Armstrong & Lab & 1525\\
Graham Seddon & LD & 807\\
Peter Stafford & BNP & 234\\
Alexander Rudkin & Grn & 84\\
\end{tabular*}

\subsubsection*{Croxteth (2) \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[18th November; 1 Lab gain from LD]}

\index{Croxteth , Liverpool@Croxteth, \emph{Liverpool}}

Death of Rose Bailey (Lab) and resignation of Phil Moffatt (LD).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Martin Cummins & Lab & 1447\\
Stephanie Till & Lab & 1424\\
Mark Coughlin & LD & 611\\
Michael Marner & LD & 479\\
Kai Andersen & SocLab & 135\\
Peter Tierney & BNP & 117\\
Barbara Bryan & SocLab & 70\\
Eleanor Pontin & Grn & 63\\
Tony Hammond & UKIP & 50\\
Paul Rimmer & EDP & 35\\
Steven McEllenborough & EDP & 33\\
Norman Coppell & C & 31\\
Brenda Coppell & C & 29\\
Michael Lane & UKIP & 19\\
\end{tabular*}

\subsection{St Helens}
\index{Saint Helens@St Helens}

\subsubsection*{Billinge and Seneley Green \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[14th October]}

\index{Billinge and Seneley Green , Saint Helens@Billinge \& Seneley Green, \emph{St Helens}}

Death of Richard Ward (Lab).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Alison Bacon & Lab & 1288\\
Elizabeth Black & C & 624\\
Thomas Gadsden & LD & 229\\
James Winstanley & BNP & 141\\
\end{tabular*}

\subsubsection*{Haydock \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[2nd December]}

\index{Haydock , Saint Helens@Haydock, \emph{St Helens}}

Death of Jim Caunce (Lab).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Anthony Burns & Lab & 1234\\
Eric Sheldon & LD & 540\\
John Cunliffe & C & 112\\
James Winstanley & BNP & 82\\
\end{tabular*}

\subsection{Wirral}
\index{Wirral}

\subsubsection*{Pensby and Thingwall \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Pensby and Thingwall , Wirral@Pensby \& Thingwall, \emph{Wirral}}

Resignation of Sarah Quinn (LD).

This by-election was combined with the 2010 ordinary election.
%; see page \pageref{PensbyThingwallWirral} for the result.

\section{South Yorkshire}

\subsection{Rotherham}
\index{Rotherham}

\subsubsection*{Sitwell \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[5th August]}

\index{Sitwell , Rotherham@Sitwell, \emph{Rotherham}}

Death of Michael Clarke (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Christopher Middleton & C & 1213\\
Judy Dalton & Lab & 864\\
David Ridgway & Ind & 252\\
John Wilkinson & UKIP & 241\\
Abdul Razaq & LD & 98\\
\end{tabular*}

\subsection{Sheffield}
\index{Sheffield}

\subsubsection*{Woodhouse \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[26th August]}

\index{Woodhouse , Sheffield@Woodhouse, \emph{Sheffield}}

Death of Marjorie Barker (Lab).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Jackie Satur & Lab & 1855\\
Joe Otten & LD & 757\\
Jonathan Arnott & UKIP & 491\\
Laurence Hayward & C & 154\\
Jordan Pont & BNP & 143\\
John Grant & Grn & 83\\
Derek Hutchinson & Ind & 58\\
\end{tabular*}

\subsubsection*{Manor Castle \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[21st October]}

\index{Manor Castle , Sheffield@Manor Castle, \emph{Sheffield}}

Death of Jan Wilson (Lab).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Terry Fox & Lab & 2092\\
Robbie Cowbury & LD & 303\\
Graham Wroe & Grn & 224\\
Christina Stark & C & 142\\
\end{tabular*}

\section{Tyne and Wear}

\subsection{Gateshead}
\index{Gateshead}

\subsubsection*{Dunston and Teams \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Dunston and Teams , Gateshead@Dunston \& Teams, \emph{Gateshead}}

Resignation of David Bollands (Lab).

This by-election was combined with the 2010 ordinary election.
%; see page \pageref{DunstonTeamsGateshead} for the result.

\subsubsection*{Lobley Hill and Bensham \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[23rd September]}

\index{Lobley Hill and Bensham , Gateshead@Lobley Hill \& Bensham, \emph{Gateshead}}

Death of Frank Donovan (Lab).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Eileen McMaster & Lab & 1120\\
Michael Ruddy & LD & 298\\
Derrick Robson & BNP & 101\\
Val Bond & C & 97\\
\end{tabular*}

\subsubsection*{Saltwell \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[23rd September]}

\index{Saltwell , Gateshead@Saltwell, \emph{Gateshead}}

Resignation of Ian Mearns (Lab).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Denise Robson & Lab & 793\\
Laura Turner & LD & 196\\
Alan Bond & C & 86\\
Janet Robson & BNP & 77\\
\end{tabular*}

\subsection{Newcastle upon Tyne}
\index{Newcastle upon Tyne}

\subsubsection*{Denton \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Denton , Newcastle upon Tyne@Denton, \emph{Newcastle upon Tyne}}

Resignation of Peter Arnold (LD).

This by-election was combined with the 2010 ordinary election.
%; see page \pageref{DentonNewcastleTyne} for the result.

\subsection{North Tyneside}
\index{North Tyneside}

\subsubsection*{Battle Hill \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[30th September]}

\index{Battle Hill , North Tyneside@Battle Hill, \emph{N. Tyneside}}

Resignation of Mary Glindon (Lab).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Lesley Spillard & Lab & 1334\\
Dorothy Bradley & LD & 826\\
Wendy Morton & C & 97\\
Dan Ellis & Ind & 43\\
\end{tabular*}

\subsection{South Tyneside}
\index{South Tyneside}

\subsubsection*{Primrose \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[25th February]}

\index{Primrose , South Tyneside@Primrose, \emph{S. Tyneside}}

Death of Barrie Scorer (Lab).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Ken Stephenson & Lab & 854\\
Pete Hodgkinson & BNP & 566\\
Aaron Luke & Ind & 213\\
David Rice & Ind & 174\\
Anthony Lanaghan & C & 124\\
Susan Troupe & LD & 100\\
\end{tabular*}

\section{West Midlands}

\subsection{Dudley}
\index{Dudley}

At the May 2010 ordinary election there was an unfilled vacancy in Sedgley ward due to the resignation of John Perry (C).
\index{Sedgley , Dudley@Sedgley, \emph{Dudley}}

\subsection{Sandwell}
\index{Sandwell}

At the May 2010 ordinary election there was an unfilled vacancy in Rowley ward due to the resignation of Bill Thomas (Lab).
\index{Sedgley , Sandwell@Sedgley, \emph{Sandwell}}

NF = National Front

\subsubsection*{Wednesbury North \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[18th November; Lab gain from C]}

\index{Wednesbury North , Sandwell@Wednesbury N., \emph{Sandwell}}

Resignation of Bill Archer (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Peter Hughes & Lab & 1322\\
Mike Warner & C & 643\\
Ade Woodhouse & NF & 76\\
Mary Wilson & LD & 45\\
Colin Bye & Grn & 42\\
\end{tabular*}

%\subsection{Solihull}
%
%\subsubsection*{Olton \hspace*{\fill}\nolinebreak[1]%
%\enspace\hspace*{\fill}
%\finalhyphendemerits=0
%[20th January]}
%
%\index{Olton , Solihull@Olton, Solihull}
%
%Death of Honor Cox (LD).
%
%\noindent
%\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
%.
%\end{tabular*}

\subsection{Walsall}
\index{Walsall}

\subsubsection*{Bloxwich West \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[15th July; Lab gain from C]}

\index{Bloxwich West , Walsall@Bloxwich W., \emph{Walsall}}

Death of Melvin Pitt (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Frederick Westley & Lab & 1142\\
Theresa Smith & C & 800\\
Paul Valdmanis & UKIP & 91\\
Christine Cockayne & LD & 71\\
Zoe Henderson & Grn & 28\\
\end{tabular*}

\subsubsection*{Rushall-Shelfield \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[11th November]}

\index{Rushall-Shelfield , Walsall@Rushall-Shelfield, \emph{Walsall}}

Death of Albert Griffiths (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Lorna Rattigan & C & 639\\
Richard Worrall & Lab & 611\\
Bill Vaughan & BNP & 141\\
Tim Melville & UKIP & 90\\
Mark Beech & Loony & 42\\
\end{tabular*}

\subsection{Wolverhampton}
\index{Wolverhampton}

\subsubsection*{Wednesfield North \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Wednesfield North , Wolverhampton@Wednesfield N., \emph{Wolverhampton}}

Resignation of Charlotte Quarmby (C).

This by-election was combined with the 2010 ordinary election.
%; see page \pageref{WednesfieldNWolverhampton} for the result.

\subsubsection*{Bilston North \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[29th July; Lab gain from C]}

\index{Bilston North , Wolverhampton@Bilston N., \emph{Wolverhampton}}

Death of Gill Fellows (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Linda Leach & Lab & 1292\\
Marlene Berry & C & 460\\
Stewart Gardner & BNP & 131\\
Barry Hodgson & UKIP & 55\\
Darren Friel & LD & 52\\
\end{tabular*}

\section{West Yorkshire}

\subsection{Bradford}
\index{Bradford}

\subsubsection*{Worth Valley \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[25th November]}

\index{Worth Valley , Bradford@Worth Valley, \emph{Bradford}}

Resignation of Kris Hopkins (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Russell Brown & C & 1020\\
Mark Curtis & Lab & 697\\
Robert Swindells & Grn & 235\\
Sharon Purvis & LD & 180\\
\end{tabular*}

\subsection{Leeds}
\index{Leeds}

\subsubsection*{Hyde Park and Woodhouse \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[18th February; Lab gain from LD]}

\index{Hyde Park and Woodhouse , Leeds@Hyde Park \& Woodhouse, \emph{Leeds}}

Death of Kabeer Hussain (LD).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Gerry Harper & Lab & 1054\\
Mike Taylor & LD & 671\\
Yasser Khalid & C & 188\\
Adele Beeson & Ind & 150\\
Christopher Foren & Grn & 140\\
\end{tabular*}

\subsubsection*{Guiseley and Rawdon \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[14th October]}

\index{Guiseley and Rawdon , Leeds@Guiseley \& Rawdon, \emph{Leeds}}

Resignation of Stuart Andrew (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Paul Wadsworth & C & 2075\\
Mike King & Lab & 1708\\
Cindy Cleasby & LD & 818\\
\end{tabular*}

\columnbreak

\subsection{Wakefield}
\index{Wakefield}

\subsubsection*{Airedale and Ferry Fryston \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[21st January]}

\index{Airedale and Ferry Fryston , Wakefield@Airedale \& Ferry Fryston, \emph{Wakefield}}

Death of Graham Phelps (Lab).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Les Shaw & Lab & 1330\\
Paul Kirby & LD & 603\\
Stephen Rogerson & BNP & 353\\
Carl Milner & C & 275\\
Jason Smart & Ind & 102\\
\end{tabular*}

\section{Bedfordshire}

\subsection{Bedford}
\index{Bedford}

\subsubsection*{Kempston North \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[24th June]}

\index{Kempston North , Bedford@Kempston N., \emph{Bedford}}

Death of Ray Oliver (Lab).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Shan Hunt & Lab & 715\\
Martin Quince & C & 384\\
Ant Caprioli & LD & 272\\
\end{tabular*}

\subsection{Luton}
\index{Luton}

\subsubsection*{South \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{South , Luton@South, \emph{Luton}}

Disqualification (non-attendance) of Michelle Kiansumba (Lab).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Keir Gale & Lab & 1493\\
Peter Banks-Smith & C & 1015\\
Richard Hayward & LD & 616\\
Lance Richardson & UKIP & 201\\
Marc Scheimann & Grn & 155\\
\end{tabular*}

\section{Berkshire}

\subsection{Bracknell Forest}
\index{Bracknell Forest}

\subsubsection*{Owlsmoor \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[25th February]}

\index{Owlsmoor , Bracknell Forest@Owlsmoor, \emph{Bracknell Forest}}

Death of Ray Simonds (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Norman Bowers & C & 508\\
Mark Thompson & LD & 238\\
Guy Gillbe & Lab & 126\\
Peter Forbes & Grn & 66\\
\end{tabular*}

\subsection{West Berkshire}
\index{West Berkshire}

\subsubsection*{Thatcham South and Crookham \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[22nd July]}

\index{Thatcham South and Crookham , West Berkshire@Thatcham S. \& Crookham, \emph{W. Berks.}}

Resignation of Terry Port (LD).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Bob Morgan & LD & 936\\
Dominic Boeck & C & 787\\
\end{tabular*}

%\subsection{Windsor and Maidenhead}
%
%\subsubsection*{Park \hspace*{\fill}\nolinebreak[1]%
%\enspace\hspace*{\fill}
%\finalhyphendemerits=0
%[6th January]}
%
%\index{Park , Windsor and Maidenhead@Park, Windsor \& Maidenhead}
%
%Resignation of Richard Gard (C).
%
%\noindent
%\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
%.
%\end{tabular*}

\subsection{Wokingham}
\index{Wokingham}

At the May 2010 ordinary election there was an unfilled vacancy in Evendons ward due to the resignation of Dennis Morgan (C).
\index{Evendons , Wokingham@Evendons, \emph{Wokingham}}

%There was an unfilled vacancy in Evendons ward at the ordinary May elections following the resignation of Dennis Morgan (C) with less than six months of his term remaining.

\subsubsection*{Maiden Erlegh \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Maiden Erlegh , Wokingham@Maiden Erlegh, \emph{Wokingham}}

Death of Chris Edmunds (C).

This by-election was combined with the 2010 ordinary election.
%; see page \pageref{MaidenErleghWokingham} for the result.

\subsubsection*{Shinfield South \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Shinfield South , Wokingham@Shinfield S., \emph{Wokingham}}

Death of Malcolm Bryant (C).

This by-election was combined with the 2010 ordinary election.
%; see page \pageref{ShinfieldSWokingham} for the result.

\section{Buckinghamshire}

\subsection{Aylesbury Vale}
\index{Aylesbury Vale}

\subsubsection*{Aylesbury Central \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[11th February]}

\index{Aylesbury Central , Aylesbury Vale@Aylesbury C., \emph{Aylesbury Vale}}

Resignation of Keith Turner (LD).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Graham Webster & LD & 354\\
Mark Winn & C & 213\\
Michael Beall & Lab & 67\\
Brian Adams & UKIP & 65\\
\end{tabular*}

\subsubsection*{Luffield Abbey \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[11th February]}

\index{Luffield Abbey , Aylesbury Vale@Luffield Abbey, \emph{Aylesbury Vale}}

Resignation of Stefan Balbuza (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Pearl Lewis & C & 343\\
John Russell & UKIP & 151\\
Ian Metherell & LD & 133\\
Mark Benson & Ind & 63\\
\end{tabular*}

\subsection{Chiltern}

\subsubsection*{Amersham on the Hill \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Amersham on the Hill , Chiltern@Amersham on the Hill, \emph{Chiltern}}

Resignation of Ronnie Lamont (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Nigel Shepherd & C & 1125\\
Howard Maitland-Jones & LD & 1073\\
Peter Harper & Lab & 203\\
\end{tabular*}

\subsubsection*{Ashley Green, Latimer and Chenies \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[21st October]}

\index{Ashley Green, Latimer and Chenies , Chiltern@Ashley Green, Latimer \& Chenies, \emph{Chiltern}}

Death of Graham Sussum (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Andrew Garth & C & 399\\
Anil Kantaria & LD & 92\\
Peter Ward & Lab & 47\\
Alan Stevens & UKIP & 11\\
\end{tabular*}

\subsubsection*{Great Missenden \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[21st October]}

\index{Great Missenden , Chiltern@Great Missenden, \emph{Chiltern}}

Resignation of Bob Swayne (Ind elected as C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Gilbert Nockles & C & 306\\
Seb Berry & LD & 281\\
Dennis Sluman & UKIP & 90\\
\end{tabular*}

\subsection{Milton Keynes}
\index{Milton Keynes}

\subsubsection*{Stony Stratford \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Stony Stratford , Milton Keynes@Stony Stratford, \emph{Milton Keynes}}

Resignation of Brin Carstens (C).

This by-election was combined with the 2010 ordinary election.
%; see page \pageref{StonyStratfordMK} for the result.

\subsection{South Bucks}
\index{South Bucks}

\subsubsection*{Burnham Church \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[26th August]}

\index{Burnham Church , South Bucks@Burnham Church, \emph{S. Bucks}}

Resignation of Nicholas Binns (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Paul Kelly & C & 459\\
Peter Price & UKIP & 276\\
David Linsdall & LD & 80\\
\end{tabular*}

\subsection{Wycombe}
\index{Wycombe}

\subsubsection*{Totteridge \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May; LD gain from C]}

\index{Totteridge , Wycombe@Totteridge, \emph{Wycombe}}

Resignation of Joel Foley (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Jen Joseph & LD & 1234\\
Lakshan Wanigasooriya & C & 1017\\
Ian Bates & Lab & 524\\
\end{tabular*}

\subsubsection*{Greater Marlow \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[15th July]}

\index{Greater Marlow , Wycombe@Greater Marlow, \emph{Wycombe}}

Disqualification (non-attendance) of Helen Wilkinson (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Dominic Barnes & C & 609\\
Mike Harris & Ind & 348\\
Kavita Mohan & LD & 195\\
\end{tabular*}

\section{Cambridgeshire}

\subsection{County Council}
\index{Cambridgeshire}

CambSoc = Cambridge Socialists

\subsubsection*{Wisbech North \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[15th April]}

\index{Wisbech North , Cambridgeshire@Wisbech N., \emph{Cambs.}}

Death of Les Sims (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Samantha Hoy & C & 548\\
David Patrick & LD & 506\\
Barry Diggle & Lab & 287\\
Paul Clapp & UKIP & 233\\
\end{tabular*}

\subsubsection*{East Chesterton \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[16th September]}

\index{East Chesterton , Cambridgeshire@East Chesterton, \emph{Cambs.}}

Resignation of Siep Wijsenbeek (LD).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.5\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Ian Manning & LD & 832\\
Gerri Bird & Lab & 663\\
Matthew Bradney & C & 334\\
Peter Pope & Grn & 117\\
Anna Gordon & CambSoc & 53\\
Peter Burkinshaw & UKIP & 37\\
\end{tabular*}

\subsection{Cambridge}
\index{Cambridge}

\subsubsection*{East Chesterton \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{East Chesterton , Cambridge@East Chesterton, \emph{Cambridge}}

Resignation of Jennifer Liddle (LD).

This by-election was combined with the 2010 ordinary election.
%; see page \pageref{EastChestertonCambridge} for the result.

\subsubsection*{Petersfield \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Petersfield , Cambridge@Petersfield, \emph{Cambridge}}

Resignation of Ben Bradnack (Lab).

This by-election was combined with the 2010 ordinary election.
%; see page \pageref{PetersfieldCambridge} for the result.

\subsubsection*{West Chesterton \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{West Chesterton , Cambridge@West Chesterton, \emph{Cambridge}}

Resignation of Diane Armstrong (LD).

This by-election was combined with the 2010 ordinary election.
%; see page \pageref{WestChestertonCambridge} for the result.

\subsubsection*{Coleridge \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[4th November; Lab gain from C]}

\index{Coleridge , Cambridge@Coleridge, \emph{Cambridge}}

Resignation of Chris Howell (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
George Owers & Lab & 900\\
Andrew Bower & C & 734\\
Sarah Barnes & LD & 223\\
Valerie Hopkins & Grn & 137\\
Albert Watts & UKIP & 53\\
\end{tabular*}

\subsection{Fenland}
\index{Fenland}

\subsubsection*{The Mills \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[4th March]}

\index{Mills , Fenland@The Mills, \emph{Fenland}}

Death of Ray German (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Robert Chambers & C & 301\\
Chris Howes & LD & 264\\
Sandra Rylance & UKIP & 58\\
Max Kelly & Lab & 33\\
\end{tabular*}

\subsubsection*{Kirkgate \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[15th April; LD gain from C]}

\index{Kirkgate , Fenland@Kirkgate, \emph{Fenland}}

Death of Les Sims (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Dave Patrick & LD & 287\\
Steve Tierney & C & 145\\
Barry Diggle & Lab & 74\\
Paul Clapp & UKIP & 54\\
\end{tabular*}

\subsection{Huntingdonshire}
\index{Huntingdonshire}

\subsubsection*{Fenstanton \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[25th February; LD gain from C]}

\index{Fenstanton , Huntingdonshire@Fenstanton, \emph{Hunts.}}

Resignation of Paul Dakers (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Colin Saunderson & LD & 391\\
David O'Neill & C & 337\\
Angela Richards & Lab & 37\\
\end{tabular*}

\section{Cheshire}

\subsection{Cheshire East}
\index{Cheshire East}

\subsubsection*{Alderley \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[30th September]}

\index{Alderley , Cheshire East@Alderley, \emph{Ches. E.}}

Death of Liz Gilliland (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Matthew Lloyd & C & 1647\\
Oliver Romain & LD & 779\\
\end{tabular*}

\subsection{Halton}
\index{Halton}

\subsubsection*{Mersey \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Mersey , Halton@Mersey, \emph{Halton}}

Death of Sue Blackmore (LD).

This by-election was combined with the 2010 ordinary election.
%; see page \pageref{MerseyHalton} for the result.

\subsection{Warrington}
\index{Warrington}

\subsubsection*{Fairfield and Howley \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Fairfield and Howley , Warrington@Fairfield \& Howley, \emph{Warrington}}

Resignation of Yvonne Fovargue (Lab).

This by-election was combined with the 2010 ordinary election.
%; see page \pageref{FairfieldHowleyWarrington} for the result.

\subsubsection*{Bewsey and Whitecross \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[9th December; Lab gain from LD]}

\index{Bewsey and Whitecross , Warrington@Bewsey \& Whitecross, \emph{Warrington}}

Resignation of Jo Crotty (LD).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Jeff Richards & Lab & 1032\\
Ann Raymond & LD & 221\\
Lance Reah & C & 118\\
Lyndsay McAteer & Grn & 47\\
John Mulhall & Ind & 33\\
\end{tabular*}

\section{Cumbria}

\subsection{County Council}
\index{Cumbria}

\subsubsection*{Longtown and Bewcastle \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Longtown and Bewcastle , Cumbria@Longtown \& Bewcastle, \emph{Cumbria}}

Resignation of Amanda Long (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Val Tarbitt & C & 1718\\
Ian Highmore & LD & 1158\\
Helen Horne & Lab & 495\\
Tony Carvell & BNP & 175\\
\end{tabular*}

\subsubsection*{Aspatria and Wharrels \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[9th September]}

\index{Aspatria and Wharrels , Cumbria@Aspatria \& Wharrels, \emph{Cumbria}}

Death of Jim Buchanan (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Mike Johnson & C & 823\\
Helen Graham & Grn & 342\\
\end{tabular*}

\subsection{Allerdale}
\index{Allerdale}

\subsubsection*{Christchurch \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[19th August]}

\index{Christchurch , Allerdale@Christchurch, \emph{Allerdale}}

Disqualification (non-attendance) of Les Lytollis (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Roy Swindells & C & 466\\
Roger Peck & LD & 131\\
Bob Edwards & Grn & 108\\
\end{tabular*}

\subsection{Carlisle}
\index{Carlisle}

EDP = English Democrats Party

\subsubsection*{Irthing \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Irthing , Carlisle@Irthing, \emph{Carlisle}}

Resignation of Ray Knapton (C).

This by-election was combined with the 2010 ordinary election.
%; see page \pageref{IrthingCarlisle} for the result.

\subsubsection*{Stanwix Urban \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[16th September]}

\index{Stanwix Urban , Carlisle@Stanwix Urban, \emph{Carlisle}}

Resignation of John Stevenson (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Paul Nedved & C & 888\\
Jackie Franklin & Lab & 488\\
Hazel Bowmaker & Grn & 96\\
Adam Pearson & EDP & 85\\
\end{tabular*}

\subsection{South Lakeland}
\index{South Lakeland}

\subsubsection*{Staveley-in-Cartmel \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Staveley-in-Cartmel , South Lakeland@Staveley-in-Cartmel, \emph{S. Lakeland}}

Resignation of Clive Leal (LD).

This by-election was combined with the 2010 ordinary election.
%; see page \pageref{StaveleyCartmelSLakeland} for the result.

\subsubsection*{Lyth Valley \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[4th November; C gain from LD]}

\index{Lyth Valley , South Lakeland@Lyth Valley, \emph{S. Lakeland}}

Resignation of Rosie Ballantyne-Smith (LD).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
John Holmes & C & 474\\
Jane Hall & LD & 451\\
Marilyn Molloy & Lab & 32\\
\end{tabular*}

\section{Derbyshire}

\subsection{Chesterfield}
\index{Chesterfield}

\subsubsection*{Brimington South \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May; Lab gain from LD]}

\index{Brimington South , Chesterfield@Brimington S., \emph{Chesterfield}}

Resignation of Helen Walsh (LD).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
John Haywood & Lab & 1500\\
Stephen Hartley & LD & 1134\\
Gary Hatton & C & 499\\
\end{tabular*}

\subsection{Derby}
\index{Derby}

At the May 2010 ordinary election there was an unfilled vacancy in Abbey ward due to the resignation of Deirdre Mitchell (LD).
\index{Abbey , Derby@Abbey, \emph{Derby}}

%There was an unfilled vacancy in Abbey ward at the ordinary May elections following the resignation of Deirdre Mitchell (LD) with less than six months of her term remaining.

\subsection{Erewash}
\index{Erewash}

\subsubsection*{West Hallam and Dale Abbey \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[21st January]}

\index{West Hallam and Dale Abbey , Erewash@West Hallam \& Dale Abbey, \emph{Erewash}}

Resignation of John Fildes (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Bruce Broughton & C & 692\\
Gary Hamson & LD & 506\\
James Dawson & Lab & 149\\
\end{tabular*}

\subsection{High Peak}
\index{High Peak}

\subsubsection*{New Mills West \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{New Mills West , High Peak@New Mills W., \emph{High Peak}}

Resignation of Stephen Sharp (LD).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Janet Carter & LD & 819\\
Jacqueline Gadd & C & 647\\
Alan Barrow & Lab & 504\\
Lancelot Dawson & Ind & 235\\
Hazel Body & Grn & 218\\
\end{tabular*}

\subsection{North East Derbyshire}
\index{North East Derbyshire}

\subsubsection*{Holmewood and Heath \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[4th February; Lab gain from LD]}

\index{Holmewood and Heath , North East Derbyshire@Holmewood \& Heath, \emph{N.E. Derbys.}}

Resignation of Jan Robinson (LD).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Lee Stone & Lab & 373\\
Derek Jason & C & 209\\
\end{tabular*}

\subsubsection*{Gosforth Valley \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[23rd September; C gain from LD]}

\index{Gosforth Valley , North East Derbyshire@Gosforth Valley, \emph{N.E. Derbys}}

Resignation of Walter Pryce (LD).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
John McGrory & C & 416\\
Robert Gachagan & Lab & 354\\
Wendy Temple & LD & 350\\
\end{tabular*}

\section{Devon}

\subsection{East Devon}
\index{East Devon}

\subsubsection*{Seaton \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Seaton , East Devon@Seaton, \emph{E, Devon}}

Resignation of Margaret Rogers (LD).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Peter Burrows & LD & 2414\\
John Meakin & C & 1795\\
\end{tabular*}

\subsection{Exeter}
\index{Exeter}

For the results of the twelve by-elections held on 9th September, following the disqualification of the councillors elected in May 2006 after the High Court ruled that their terms had expired, and the further by-election in Topsham on that day following the resignation of Mark Starling (C), see
\url{https://www.andrewteale.me.uk/u172}.
%pages \pageref{ExeterStart} to \pageref{ExeterEnd}.

\subsubsection*{Pennsylvania \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Pennsylvania , Exeter@Pennsylvania, \emph{Exeter}}

Resignation of Alexander Bond (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
	Tim Payne & LD & 1391\\
	David Thompson & C & 913\\
	Bernard Dugdale & Lab & 491\\
	David Smith & UKIP & 152\\
	Isaac Price-Sosner & Grn & 88\\
\end{tabular*}

Due to Exeter's failed conversion to unitary status this by-election ended up being the ordinary election in Pennsylvania for the term 2010--14.

\subsection{Mid Devon}
\index{Mid Devon}

\subsubsection*{Yeo \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[25th February; C gain from LD]}

\index{Yeo , Mid Devon@Yeo, \emph{Mid Devon}}

Death of David Pullen (LD).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Derek Coren & C & 714\\
Peter Heal & LD & 489\\
\end{tabular*}

\subsection{Plymouth}
\index{Plymouth}

\subsubsection*{Efford and Lipson \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Efford and Lipson , Plymouth@Efford \& Lipson, \emph{Plymouth}}

Resignation of Bernard Miller (Lab).

This by-election was combined with the 2010 ordinary election.
%; see page \pageref{EffordLipsonPlymouth} for the result.

\subsection{South Hams}
\index{South Hams}

\subsubsection*{Ivybridge Filham \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[18th February; LD gain from C]}

\index{Ivybridge Filham , South Hams@Ivybridge Filham, \emph{S. Hams}}

Resignation of Terry Hewitt (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Tony Barber & LD & 379\\
Alan Wright & C & 356\\
Helen Eassom & Lab & 121\\
\end{tabular*}

\subsection{Teignbridge}
\index{Teignbridge}

\subsubsection*{Ipplepen \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[23rd September; LD gain from C]}

\index{Ipplepen , Teignbridge@Ipplepen, \emph{Teignbridge}}

Death of Victor Elliott (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Alistair Dewhirst & LD & 756\\
Phil Coombes & C & 458\\
\end{tabular*}

\subsection{Torbay}
\index{Torbay}

\subsubsection*{St Mary's-with-Summercombe \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[22nd July; LD gain from C]}

\index{Saint Mary's-with-Summercombe , Torbay@St Mary's-with-Summercombe, \emph{Torbay}}

Death of Stuart John (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Andrew Baldrey & LD & 801\\
Nicholas Henderson & C & 365\\
Rosemary Clarke & Lab & 195\\
Jen Walsh & UKIP & 159\\
\end{tabular*}

\section{Dorset}

\subsection{East Dorset}
\index{East Dorset}

\subsubsection*{Corfe Mullen South \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[15th July]}

\index{Corfe Mullen South , East Dorset@Corfe Mullen S., \emph{E. Dorset}}

Resignation of Stewart Hearn (LD).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Phil Harknett & LD & 478\\
Brian Lane & C & 350\\
Josephine Evans & UKIP & 34\\
\end{tabular*}

\subsection{Poole}
\index{Poole}

Poole = Poole People

\subsubsection*{Broadstone \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Broadstone , Poole@Broadstone, \emph{Poole}}

Resignation of Daniel Martin (LD).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Roy Godfrey & LD & 3018\\
Ruth Bessant & C & 2971\\
Jack Edwards & UKIP & 295\\
John Hewinson & Lab & 277\\
\end{tabular*}

\subsubsection*{Newtown \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[9th September]}

\index{Newtown , Poole@Newtown, \emph{Poole}}

Resignation of Michael Plummer (LD).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Jo Clements & LD & 809\\
Tony Reeves & C & 481\\
Jason Sanderson & Lab & 205\\
Diana Butler & UKIP & 114\\
William Kimmet & BNP & 66\\
\end{tabular*}

\subsubsection*{Poole Town \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[2nd December; Poole gain from C]}

\index{Poole Town , Poole@Poole Town, \emph{Poole}}

Death of Brian Leverett (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Mark Howell & Poole & 463\\
Anthony Reeves & C & 438\\
Peter England & LD & 213\\
Jason Sanderson & Lab & 201\\
Avril King & UKIP & 55\\
William Kimmet & BNP & 32\\
\end{tabular*}

\section{County Durham}

\subsection{Darlington}
\index{Darlington}

\subsubsection*{Cockerton West \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[8th July]}

\index{Cockerton West , Darlington@Cockerton W., \emph{Darlington}}

Resignation of Jenny Chapman (Lab).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Jan Cossins & Lab & 388\\
Brian Jefferson & LD & 347\\
David Davies & C & 84\\
Paul Thompson & BNP & 41\\
\end{tabular*}

\subsection{Durham}
\index{Durham}

\subsubsection*{Easington \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[11th February]}

\index{Easington , Durham@Easington, \emph{Durham}}

Death of Richard Burnip (Lab).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Alan Barker & Lab & 702\\
Terry Murray & Ind & 311\\
Carole Harrison & LD & 126\\
Margaret Reid & C & 120\\
\end{tabular*}

\subsubsection*{Brandon \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[30th September]}

\index{Brandon , Durham@Brandon, \emph{Durham}}

Death of Ronnie Rodgers (Lab).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
John Turnbull & Lab & 1204\\
Maureen Smith & LD & 538\\
Mark Krajewski & C & 140\\
\end{tabular*}

\subsubsection*{Deneside \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[14th October]}

\index{Deneside , Durham@Deneside, \emph{Durham}}

Death of Albert Nugent (Lab).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Jennifer Bell & Lab & 917\\
Margaret Reid & C & 196\\
\end{tabular*}

%\subsection{Stockton-on-Tees}
%
%IBIS = Ingleby Barwick Independent Society
%
%Thornaby = Thornaby Independent Association
%
%\subsubsection*{Billingham East \hspace*{\fill}\nolinebreak[1]%
%\enspace\hspace*{\fill}
%\finalhyphendemerits=0
%[tba]}
%
%\index{Billingham East , Stockton-on-Tees@Billingham E., Stockton-on-Tees}
%
%Resignation of Alex Cunningham (Lab).
%
%\noindent
%\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
%.
%\end{tabular*}
%
%\subsubsection*{Ingleby Barwick East \hspace*{\fill}\nolinebreak[1]%
%\enspace\hspace*{\fill}
%\finalhyphendemerits=0
%[tba]}
%
%\index{Ingleby Barwick East , Stockton-on-Tees@Ingleby Barwick E., Stockton-on-Tees}
%
%Resignation of Andrew Larkin (IBIS).
%
%\noindent
%\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
%.
%\end{tabular*}
%
%\subsubsection*{Mandale and Victoria \hspace*{\fill}\nolinebreak[1]%
%\enspace\hspace*{\fill}
%\finalhyphendemerits=0
%[tba]}
%
%\index{Mandale and Victoria , Stockton-on-Tees@Mandale \& Victoria, Stockton-on-Tees}
%
%Death of Allison Trainer (Thornaby).
%
%\noindent
%\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
%.
%\end{tabular*}

\section{East Sussex}

\subsection{Brighton and Hove}
\index{Brighton and Hove}

\subsubsection*{St Peter's and North Laine  \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[8th July]}

\index{Saint Peter's and North Laine , Brighton and Hove@St Peter's \& N. Laine, \emph{Brighton \& Hove}}

Resignation of Keith Taylor (Grn).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Lizzie Deane & Grn & 1816\\
Tom French & Lab & 880\\
Rob Buckwell & C & 365\\
Trefor Hunter & LD & 103\\
Gerald O'Brien & Ind & 32\\
\end{tabular*}

\subsection{Hastings}
\index{Hastings}

\subsubsection*{Hollington \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Hollington , Hastings@Hollington, \emph{Hastings}}

Resignation of Terry Soan (Lab).

This by-election was combined with the 2010 ordinary election.
%; see page \pageref{HollingtonHastings} for the result.

\subsubsection*{Ore \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[17th June; Lab gain from C]}

\index{Ore , Hastings@Ore, \emph{Hastings}}

Ordinary election postponed from 6th May; death of outgoing councillor Roy Tucker (C) who had been nominated for re-election.

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Michael Wincott & Lab & 608\\
Stuart Padget & C & 475\\
Anne Scott & LD & 158\\
Nick Prince & BNP & 33\\
\end{tabular*}

\subsection{Wealden}
\index{Wealden}

\subsubsection*{Heathfield North and Central \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[23rd September]}

\index{Heathfield North and Central , Wealden@Heathfield N. \& C., \emph{Wealden}}

Death of Niki Oakes (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Peter Newnham & C & 802\\
Jim Benson & LD & 357\\
\end{tabular*}

\section{East Yorkshire}

\subsection{East Riding}
\index{East Riding}

\subsubsection*{Willerby and Kirk Ella \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May; LD gain from C]}

\index{Willerby and Kirk Ella , East Riding@Willerby \& Kirk Ella, \emph{E. Riding}}

Resignation of Kerry Hemming-Tayler (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Fred Smith & LD & 5107\\
Josh Newlove & Lab & 1298\\
\end{tabular*}

\subsection{Kingston upon Hull}
\index{Kingston upon Hull}

\subsubsection*{Bransholme West \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Bransholme West , Kingston upon Hull@Bransholme W., \emph{Kingston upon Hull}}

Resignation of Gordon Wilson (Lab).

This by-election was combined with the 2010 ordinary election.
%; see page \pageref{BransholmeWHull} for the result.

\subsubsection*{Bricknell \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Bricknell , Kingston upon Hull@Bricknell, \emph{Kingston upon Hull}}

Resignation of Andrew Percy (C).

This by-election was combined with the 2010 ordinary election.
%; see page \pageref{BricknellHull} for the result.

\section{Essex}

\subsection{Basildon}
\index{Basildon}

\subsubsection*{Nethermayne \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[22nd July]}

\index{Nethermayne , Basildon@Nethermayne, \emph{Basildon}}

Resignation of Ben Williams (LD).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Phil Jenkins & LD & 605\\
David Kirkman & Lab & 461\\
Stephen Foster & C & 372\\
Kerry Smith & UKIP & 280\\
Irene Bateman & BNP & 70\\
Jason Richardson & Ind & 18\\
\end{tabular*}

\subsection{Braintree}
\index{Braintree}

\subsubsection*{Braintree South \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[24th June]}

\index{Braintree South , Braintree@Braintree S., \emph{Braintree}}

Disqualification (non-attendance) of Russell Wilkins (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Abi Olumbori & C & 351\\
Gordon Currie & Lab & 316\\
David Toombs & LD & 216\\
Andy Beatty & Ind & 138\\
Wendy Partridge & Grn & 44\\
\end{tabular*}

\subsection{Brentwood}
\index{Brentwood}

\subsubsection*{Pilgrims Hatch \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Pilgrims Hatch , Brentwood@Pilgrims Hatch, \emph{Brentwood}}

Resignation of Mathew Aspinell (LD).

This by-election was combined with the 2010 ordinary election.
%; see page \pageref{PilgrimsHatchBrentwood} for the result.

\subsection{Epping Forest}
\index{Epping Forest}

\subsubsection*{\sloppyword{Chipping Ongar, Greensted and Marden Ash} \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Chipping Ongar, Greensted and Marden Ash , Epping Forest@Chipping Ongar, Greensted \& Marden Ash, \emph{Epping Forest}}

Resignation of Glyn Pritchard (C).

This by-election was combined with the 2010 ordinary election.
%; see page \pageref{ChippingOngarGreenstedMardenAshEppingForest} for the result.

\subsection{Rochford}
\index{Rochford}

EDP = English Democrats Party

\subsubsection*{Wheatley \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[15th July]}

\index{Wheatley , Rochford@Wheatley, \emph{Rochford}}

Death of John Pullen (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Aron Priest & C & 417\\
John Hayter & EDP & 142\\
Sid Cumberland & LD & 78\\
David Bodimeade & Lab & 47\\
\end{tabular*}

\subsection{Southend-on-Sea}
\index{Southend-on-Sea}

At the May 2010 ordinary election there was an unfilled vacancy in Milton ward due to the death of Ann Robertson (C).
\index{Milton , Southend-on-Sea@Milton, \emph{Southend-on-Sea}}

%There was an unfilled vacancy in Milton ward at the ordinary May elections following the death of Ann Robertson (C) with less than six months of her term remaining.

\subsection{Tendring}
\index{Tendring}

Tendring = Tendring First

\subsubsection*{Golf Green \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[8th April; Lab gain from Tendring]}

\index{Golf Green , Tendring@Golf Green, \emph{Tendring}}

Death of Ray Smith (Tendring).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.53\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Dan Casey & Lab & 409\\
John Chittock & C & 404\\
Louise Stanley & Tendring & 313\\
Keith Beaumont & BNP & 139\\
Christopher Judd & Ind & 120\\
John Candler & LD & 63\\
\end{tabular*}

\section{Gloucestershire}

%\subsection{County Council}
%
%\subsubsection*{Rodborough \hspace*{\fill}\nolinebreak[1]%
%\enspace\hspace*{\fill}
%\finalhyphendemerits=0
%[tba]}
%
%\index{Rodborough , Gloucestershire@Rodborough, Glos.}
%
%Death of Stephen Glanfield (C).
%
%\noindent
%\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
%.
%\end{tabular*}

\subsection{Cheltenham}
\index{Cheltenham}

\subsubsection*{Oakley \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Oakley , Cheltenham@Oakley, \emph{Cheltenham}}

Resignation of Martin Dunne (LD).

This by-election was combined with the 2010 ordinary election.
%; see page \pageref{OakleyCheltenham} for the result.

\subsubsection*{Springbank \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Springbank , Cheltenham@Springbank, \emph{Cheltenham}}

Resignation of Simon Wheeler (LD).

This by-election was combined with the 2010 ordinary election.
%; see page \pageref{SpringbankCheltenham} for the result.

\subsubsection*{Springbank \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[28th October]}

\index{Springbank , Cheltenham@Springbank, \emph{Cheltenham}}

Death of John Morris (LD).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Christopher Coleman & LD & 722\\
Mireille Weller & C & 188\\
Clive Harriss & Lab & 142\\
Jon Stubbings & Grn & 35\\
\end{tabular*}

\subsection{Gloucester}
\index{Gloucester}

At the May 2010 ordinary election there was an unfilled vacancy in Barton and Tredworth ward due to the death of Yakub Pandor (C).
\index{Barton and Tredworth , Gloucester@Barton \& Tredworth, \emph{Gloucester}}

\subsection{Stroud}
\index{Stroud}

\subsubsection*{Berkeley \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Berkeley , Stroud@Berkeley, \emph{Stroud}}

Resignation of Tim Archer (C).

This by-election was combined with the 2010 ordinary election.
%; see page \pageref{BerkeleyStroud} for the result.

%\subsubsection*{Amberley and Woodchester \hspace*{\fill}\nolinebreak[1]%
%\enspace\hspace*{\fill}
%\finalhyphendemerits=0
%[tba]}
%
%\index{Amberley and Woodchester , Stroud@Amberley \& Woodchester, Stroud}
%
%Death of Stephen Glanfield (C).
%
%\noindent
%\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
%.
%\end{tabular*}

\section{Hampshire}

\subsection{County Council}
\index{Hampshire}

\subsubsection*{Andover South \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[21st October]}

\index{Andover South , Hampshire@Andover S., \emph{Hants.}}

Death of David Kirk (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
David Drew & C & 1183\\
Leonard Gates & LD & 1111\\
John Newland & Lab & 245\\
Anthony McCabe & UKIP & 233\\
\end{tabular*}

\subsection{Fareham}
\index{Fareham}

\subsubsection*{Fareham West \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[9th December; LD gain from C]}

\index{Fareham West , Fareham@Fareham W., \emph{Fareham}}

Resignation of Diana Harrison (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Nick Gregory & LD & 933\\
Stephen Day & C & 687\\
Michael Prior & Lab & 124\\
Steve Richards & UKIP & 93\\
Peter Doggett & Grn & 35\\
\end{tabular*}

\subsection{Gosport}
\index{Gosport}

At the May 2010 ordinary election there was an unfilled vacancy in Christchurch ward due to the death of Jackie Carr (LD).
\index{Christchurch , Gosport@Christchurch, \emph{Gosport}}

%There was an unfilled vacancy in Christchurch ward at the ordinary May elections following the death of Jackie Carr (LD) with less than six months of his term remaining.

\subsection{Havant}
\index{Havant}

\subsubsection*{Hayling East \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Hayling East , Havant@Hayling E., \emph{Havant}}

Resignation of Sheila Pearce (C).

This by-election was combined with the 2010 ordinary election.
%; see page \pageref{HaylingEHavant} for the result.

%\subsection{New Forest}
%
%\subsubsection*{Marchwood \hspace*{\fill}\nolinebreak[1]%
%\enspace\hspace*{\fill}
%\finalhyphendemerits=0
%[tba]}
%
%\index{Marchwood , New Forest@Marchwood, New Forest}
%
%Death of Alan Shotter (C).
%
%\noindent
%\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
%.
%\end{tabular*}

\subsection{Rushmoor}
\index{Rushmoor}

\subsubsection*{Wellington \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[23rd September]}

\index{Wellington , Rushmoor@Wellington, \emph{Rushmoor}}

Resignation of Francis Williams (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Attika Choudhary & C & 270\\
Mitch Manning & LD & 238\\
Sam Wines & Lab & 184\\
Eddie Poole & UKIP & 50\\
Roger Watkins & Ind & 12\\
\end{tabular*}

\subsection{Test Valley}
\index{Test Valley}

\subsubsection*{Anna \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Anna , Test Valley@Anna, \emph{Test Valley}}

Resignation of Arthur Peters (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Maureen Flood & C & 1804\\
Anthony Evans & LD & 836\\
Anthony McCabe & UKIP & 202\\
\end{tabular*}

\subsection{Winchester}
\index{Winchester}

\subsubsection*{St Paul \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[14th October]}

\index{Saint Paul , Winchester@St Paul, \emph{Winchester}}

Resignation of Karen Barratt (LD).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Robert Hutchison & LD & 968\\
Helen Osborne & C & 606\\
Nigel Fox & Lab & 247\\
\end{tabular*}

%\subsubsection*{Oliver's Battery and Badger Farm \hspace*{\fill}\nolinebreak[1]%
%\enspace\hspace*{\fill}
%\finalhyphendemerits=0
%[tba]}
%
%\index{Oliver's Battery and Badger Farm , Winchester@Oliver's Battery \& Badger Farm, Winchester}
%
%Death of David Spender (LD).
%
%\noindent
%\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
%.
%\end{tabular*}

\columnbreak

\section{Herefordshire}
\index{Herefordshire}

IOCH = It's Our County (Herefordshire)

\subsubsection*{Hope End \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Hope End , Herefordshire@Hope End, \emph{Herefs.}}

Resignation of Rees Mills (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Tony Johnson & C & 1703\\
Barry Ashton & LD & 1651\\
\end{tabular*}

\subsubsection*{Ledbury \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Ledbury , Herefordshire@Ledbury, \emph{Herefs.}}

Resignation of Kay Swinburne (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Phil Bettington & C & 2438\\
Michael Gogan & LD & 1769\\
Robert Wilson & Ind & 713\\
\end{tabular*}

\subsubsection*{St Nicholas \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[14th October; IOCH gain from Ind]}

\index{Saint Nicholas , Herefordshire@St Nicholas, \emph{Herefs.}}

Death of David Benjamin (Ind).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Justin Lavender & IOCH & 589\\
Anthony Murphy & LD & 385\\
Colin Mears & Ind & 173\\
Vivienne Jones & C & 156\\
\end{tabular*}

\section{Hertfordshire}

\subsection{County Council}
\index{Hertfordshire}

\subsubsection*{St Albans South \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[3rd June]}

\index{Saint Albans South , Hertfordshire@St Albans S., \emph{Herts.}}

Death of Mike Ellis (LD).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Martin Frearson & LD & 1482\\
Salih Gaygusuz & C & 1250\\
Iain Grant & Lab & 540\\
Kate Metcalf & Ind & 249\\
\end{tabular*}

\subsection{Dacorum}
\index{Dacorum}

\subsubsection*{Adeyfield West \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[11th March]}

\index{Adeyfield West , Dacorum@Adeyfield W., \emph{Dacorum}}

Death of Keith Reid (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Dan Wood & C & 486\\
Sue White & Lab & 429\\
Steve Wilson & LD & 362\\
Janet Price & BNP & 203\\
\end{tabular*}

\subsubsection*{Aldbury and Wigginton \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[26th August; LD gain from C]}

\index{Aldbury and Wigginton , Dacorum@Aldbury \& Wigginton, \emph{Dacorum}}

Disqualification (non-attendance) of Mike Edwards (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Rosemarie Hollinghurst & LD & 593\\
Paul Richardson & C & 305\\
Thomas Wright & Lab & 18\\
\end{tabular*}

\subsection{East Hertfordshire}
\index{East Hertfordshire}

\subsubsection*{Hunsdon \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[11th November]}

\index{Hunsdon , East Hertfordshire@Hunsdon, \emph{E. Herts.}}

Resignation of Deborah Clark (Ind).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Michael Newman & Ind & 339\\
Geoffrey Williamson & C & 206\\
Linda Harvey & Lab & 31\\
\end{tabular*}

\subsubsection*{Sawbridgeworth \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[23rd December]}

\index{Sawbridgeworth , East Hertfordshire@Sawbridgeworth, \emph{E. Herts.}}

Resignation of Nigel Clark (Ind).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Eric Buckmaster & Ind & 441\\
William Mortimer & C & 343\\
Peter Mitchell & Lab & 99\\
Michael Shaw & LD & 95\\
\end{tabular*}

\subsection{North Hertfordshire}
\index{North Hertfordshire}

\subsubsection*{Royston Palace \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Royston Palace , North Hertfordshire@Royston Palace, \emph{N. Herts}}

Resignation of Liz Beardwell (LD).

This by-election was combined with the 2010 ordinary election.
%; see page \pageref{RoystonPalaceNHerts} for the result.

\subsection{St Albans}
\index{Saint Albans@St Albans}

\subsubsection*{Ashley \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[3rd June]}

\index{Ashley , Saint Albans@Ashley, \emph{St Albans}}

Death of Mike Ellis (LD).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Andy Grant & LD & 774\\
John Paton & Lab & 354\\
Christopher Baker & C & 342\\
Graham Ward & Grn & 93\\
\end{tabular*}

\subsection{Watford}
\index{Watford}

\subsubsection*{Central \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[14th October]}

\index{Central , Watford@Central, \emph{Watford}}

Resignation of Sheila Smillie (LD).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Helen Lynch & LD & 696\\
Fred Grindrod & Lab & 622\\
Youseffe Fahmy & C & 158\\
Dorothy Nixon & Grn & 79\\
Dan Channing & UKIP & 24\\
\end{tabular*}

\subsection{Welwyn Hatfield}
\index{Welwyn Hatfield}

\subsubsection*{Hatfield Villages \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Hatfield Villages , Welwyn Hatfield@Hatfield Villages, \emph{Welwyn Hatfield}}

Resignation of Mark Gilding (C).

This by-election was combined with the 2010 ordinary election.
%; see page \pageref{HatfieldVillagesWelwynHatfield} for the result.

\subsubsection*{Northaw and Cuffley \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Northaw and Cuffley , Welwyn Hatfield@Northaw \& Cuffley, \emph{Welwyn Hatfield}}

Death of John Mansfield (C).

This by-election was combined with the 2010 ordinary election.
%; see page \pageref{NorthawCuffleyWelwynHatfield} for the result.

\section{Isle of Wight}
\index{Isle of Wight}

\subsubsection*{Ryde South \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[27th May; C gain from LD]}

\index{Ryde South , Isle of Wight@Ryde S., \emph{Isle of Wight}}

Disqualification (sentenced to three months in prison, suspended, assaulting a police officer) of Adrian Whittaker (Ind elected as LD).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Gary Taylor & C & 274\\
Deborah Gardiner & Lab & 201\\
Tony Zeid & LD & 164\\
Ian Jenkins & Ind & 97\\
\end{tabular*}

\subsubsection*{Chale, Niton and Whitwell \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[11th November]}

\index{Chale, Niton and Whitwell , Isle of Wight@Chale, Niton \& Whitwell, \emph{Isle of Wight}}

Resignation of William Myatt-Willington (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Dave Stewart & C & 510\\
Malcolm Groves & LD & 365\\
Josh Cooper & Lab & 76\\
\end{tabular*}

\section{Kent}

EDP = English Democrats Party

\subsection{County Council}
\index{Kent}

\subsubsection*{Dover Town \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[16th December; Lab gain from C]}

\index{Dover Town , Kent@Dover Town, \emph{Kent}}

Death of Roger Frayne (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Gordon Cowan & Lab & 1491\\
Patrick Sherratt & C & 1348\\
Victor Matcham & UKIP & 404\\
John Trickey & LD & 170\\
\end{tabular*}

%\subsubsection*{Romney Marsh \hspace*{\fill}\nolinebreak[1]%
%\enspace\hspace*{\fill}
%\finalhyphendemerits=0
%[tba]}
%
%\index{Romney Marsh , Dover@Romney Marsh, Dover}
%
%Death of Willie Richardson (C).
%
%\noindent
%\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
%.
%\end{tabular*}

%\subsubsection*{Tonbridge \hspace*{\fill}\nolinebreak[1]%
%\enspace\hspace*{\fill}
%\finalhyphendemerits=0
%[20th January]}
%
%\index{Tonbridge , Dover@Tonbridge, Dover}
%
%Death of Godfrey Horne (C).
%
%\noindent
%\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
%.
%\end{tabular*}

\subsection{Dover}
\index{Dover}

\subsubsection*{Lydden and Temple Ewell \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[16th December]}

\index{Lydden and Temple Ewell , Dover@Lydden \& Temple Ewell, \emph{Dover}}

Death of Roger Frayne (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Geoffrey Lymer & C & 239\\
Peter Walker & Lab & 90\\
Victor Matcham & UKIP & 55\\
\end{tabular*}

\subsection{Gravesham}
\index{Gravesham}

\subsubsection*{Meopham South and Vigo \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[18th March]}

\index{Meopham South and Vigo , Gravesham@Meopham S. \& Vigo, \emph{Gravesham}}

Death of Raymonde Collins (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Derek Shelbrooke & C & 515\\
Geoffrey Clark & UKIP & 122\\
Douglas Christie & Lab & 114\\
Ann O'Brien & LD & 114\\
\end{tabular*}

\subsection{Medway}
\index{Medway}

\subsubsection*{River \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[12th August; C gain from Lab]}

\index{River , Medway@River, \emph{Medway}}

Resignation of Bill Esterston (Lab).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
David Craggs & C & 617\\
John Jones & Lab & 544\\
Garry Harrison & LD & 104\\
Steven Keevil & Grn & 45\\
Brian Ravenscroft & BNP & 39\\
Ron Sands & EDP & 33\\
\end{tabular*}

\subsubsection*{River \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[21st October; Lab gain from C]}

\index{River , Medway@River, \emph{Medway}}

Resignation of David Craggs (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
John Jones & Lab & 695\\
Andrew Mackness & C & 631\\
Garry Harrison & LD & 92\\
Anthony Cook & UKIP & 42\\
Steven Keevil & Grn & 36\\
Ron Sands & EDP & 31\\
\end{tabular*}

\subsection{Swale}
\index{Swale}

\subsubsection*{Queenborough and Halfway \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Queenborough and Halfway , Swale@Queenborough \& Halfway, \emph{Swale}}

Resignation of Paul Hayes (C).

This by-election was combined with the 2010 ordinary election.
%; see page \pageref{QueenboroughHalfwaySwale} for the result.

\subsection{Tunbridge Wells}
\index{Tunbridge Wells}

\subsubsection*{St James' \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[7th October]}

\index{Saint James' , Tunbridge Wells@St James', \emph{Tunbridge Wells}}

Resignation of Mary Lewis (LD).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Benjamin Chapelard & LD & 649\\
Robert Rutherford & C & 294\\
Richard Leslie & Grn & 103\\
\end{tabular*}

\subsubsection*{Sherwood \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[16th December]}

\index{Sherwood , Tunbridge Wells@Sherwood, \emph{Tunbridge Wells}}

Death of Ted Jolley (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Robert Backhouse & C & 422\\
Alan Bullion & LD & 174\\
Ian Carvell & Lab & 124\\
Victor Webb & UKIP & 92\\
Joanna Stanley & EDP & 75\\
\end{tabular*}

\section{Lancashire}

\subsection{County Council}
\index{Lancashire}

\subsubsection*{Burnley Central East \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May; Lab gain from LD]}

\index{Burnley Central East , Lancashire@Burnley C.E., \emph{Lancs.}}

Death of Bill Bennett (LD).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Misfar Hassan & Lab & 3157\\
Martin Smith & LD & 2279\\
Paul McDevitt & BNP & 868\\
Matthew Isherwood & C & 815\\
\end{tabular*}

\subsection{Blackburn with Darwen}
\index{Blackburn with Darwen}

\subsubsection*{Queen's Park \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[4th February; Lab gain from LD]}

\index{Queen's Park , Blackburn with Darwen@Queen's Park, \emph{Blackburn with Darwen}}

Resignation of Yusuf Sidat (Ind elected as LD).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Mustafa Desai & Lab & 638\\
Imtiaz Patel&LD&366\\
Asghar Ali&C&174\\
\end{tabular*}

%\subsection{Blackpool}
%
%\subsubsection*{Stanley \hspace*{\fill}\nolinebreak[1]%
%\enspace\hspace*{\fill}
%\finalhyphendemerits=0
%[tba]}
%
%\index{Stanley , Blackpool@Stanley, Blackpool}
%
%Death of Jean Kenrick (C).
%
%\noindent
%\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
%.
%\end{tabular*}

\subsection{Burnley}
\index{Burnley}

\subsubsection*{Queensgate \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Queensgate , Burnley@Queensgate, \emph{Burnley}}

Death of Bill Bennett (LD).

This by-election was combined with the 2010 ordinary election.
%; see page \pageref{QueensgateBurnley} for the result.

\subsection{Fylde}
\index{Fylde}

\subsubsection*{Ribby-with-Wrea \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[1st July; C gain from Ind]}

\index{Ribby-with-Wrea , Fylde@Ribby-with-Wrea, \emph{Fylde}}

Death of Lyndsay Greening (Ind).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Frank Andrews & C & 292\\
Janet Wardell & Ind & 256\\
David Hobson & Grn & 11\\
\end{tabular*}

\subsubsection*{Kilnhouse \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[9th September; LD gain from C]}

\index{Kilnhouse , Fylde@Kilnhouse, \emph{Fylde}}

Death of John Prestwich (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Karen Henshaw & LD & 529\\
Matthew Lardner & C & 459\\
Peter Stephenson & Lab & 165\\
Ian Roberts & Grn & 29\\
\end{tabular*}

\subsection{Hyndburn}
\index{Hyndburn}

\subsubsection*{Peel \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[1st July]}

\index{Peel , Hyndburn@Peel, \emph{Hyndburn}}

Resignation of Graham Jones (Lab).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Wendy Dwyer & Lab & 592\\
Daniel Cassidy & C & 189\\
\end{tabular*}

\subsubsection*{Baxenden \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[18th November]}

\index{Baxenden , Hyndburn@Baxenden, \emph{Hyndburn}}

Death of John Griffiths (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Terence Hurn & C & 693\\
David Hartley & Lab & 434\\
Lesley Wolstencroft & Ind & 47\\
Munzoor Anwar & UKIP & 17\\
\end{tabular*}

\subsection{Lancaster}
\index{Lancaster}

MBI = Morecambe Bay Independents

\subsubsection*{John O'Gaunt \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[1st April]}

\index{John O'Gaunt , Lancaster@John O'Gaunt, \emph{Lancaster}}

Resignation of Jim Blakely (Lab).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Elizabeth Scott & Lab & 603\\
Harry Armistead & LD & 389\\
Ian Chamberlain & Grn & 339\\
Billy Hill & C & 301\\
Fred McGlade & UKIP & 83\\
\end{tabular*}

\subsubsection*{Skerton West \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Skerton West , Lancaster@Skerton W., \emph{Lancaster}}

Resignation of Robert Smith (Lab).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
John Harrison & Lab & 1127\\
Richard Rollins & C & 731\\
David Taylor & LD & 535\\
Paul Andrews & Grn & 184\\
\end{tabular*}

\subsubsection*{Harbour \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[7th October]}

\index{Harbour , Lancaster@Harbour, \emph{Lancaster}}

Death of John Barnes (MBI).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Geoff Walker & MBI & 287\\
Elliot Layfield & C & 161\\
Fred McGlade & UKIP & 86\\
Ian Clift & LD & 68\\
\end{tabular*}

\subsection{Pendle}
\index{Pendle}

At the May 2010 ordinary election there was an unfilled vacancy in Brierfield ward due to the resignation of Naseem Shabnam (LD).
\index{Brierfield , Pendle@Brierfield, \emph{Pendle}}

%There was an unfilled vacancy in Brierfield ward at the ordinary May elections following the resignation of Naseem Shabnam (LD) with less than six months of her term remaining.

\subsection{Preston}
\index{Preston}

\subsubsection*{Riversway \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Riversway , Preston@Riversway, \emph{Preston}}

Resignation of Jack Davenport (Lab).

This by-election was combined with the 2010 ordinary election.
%; see page \pageref{RiverswayPreston} for the result.

\subsubsection*{Riversway \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[15th July; Lab gain from LD]}

\index{Riversway , Preston@Riversway, \emph{Preston}}

Resignation of Lam Pennington (LD).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Linda Crompton & Lab & 890\\
Stephen Wilkinson & LD & 388\\
Adam Vardey & Grn & 56\\
\end{tabular*}

\subsubsection*{Cadley \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[16th September]}

\index{Cadley , Preston@Cadley, \emph{Preston}}

Resignation of Mike Onyon (LD).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
John Potter & LD & 721\\
John Young & Lab & 476\\
David Walker & C & 465\\
\end{tabular*}

\subsection{Rossendale}
\index{Rossendale}

CFirst = Community First

\subsubsection*{Healey and Whitworth \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[7th October]}

\index{Healey and Whitworth , Rossendale@Healey \& Whitworth, \emph{Rossendale}}

Resignation of Roger Wilson (Lab).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Sean Serridge & Lab & 346\\
David Bradbury & CFirst & 165\\
Marie Gibbons & C & 156\\
Clive Laight & LD & 10\\
\end{tabular*}

\subsubsection*{Irwell \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[7th October; Lab gain from C]}

\index{Irwell , Rossendale@Irwell, \emph{Rossendale}}

Resignation of Michael Christie (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Helen Jackson & Lab & 277\\
Elizabeth Heath & C & 220\\
Bill Jackson & LD & 183\\
Tina Durkin & CFirst & 64\\
\end{tabular*}

\subsection{South Ribble}
\index{South Ribble}

\subsubsection*{Moss Side \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Moss Side , South Ribble@Moss Side, \emph{S. Ribble}}

Resignation of Frank Duxbury (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Caroline Moon & C & 1088\\
Ken Jones & Lab & 731\\
\end{tabular*}

\subsection{West Lancashire}
\index{West Lancashire}

\subsubsection*{Scott \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Scott , West Lancashire@Scott, \emph{W. Lancs.}}

Resignation of Geoff Hammond (C).

This by-election was combined with the 2010 ordinary election.
%; see page \pageref{ScottWLancs} for the result.

\subsubsection*{Skelmersdale South \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[2nd September]}

\index{Skelmersdale South , West Lancashire@Skelmersdale S., \emph{W. Lancs.}}

Death of Doreen Saxon (Lab).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Nicola Roberts & Lab & 644\\
Sarah Ainscough & C & 122\\
Mike Brennan & UKIP & 105\\
\end{tabular*}

\subsubsection*{Upholland \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[2nd September]}

\index{Upholland , West Lancashire@Upholland, \emph{W. Lancs.}}

Death of Terry Rice (Lab).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
John Fillis & Lab & 749\\
David Sudworth & C & 597\\
Gary McNulty & UKIP & 118\\
\end{tabular*}

%\subsubsection*{Derby \hspace*{\fill}\nolinebreak[1]%
%\enspace\hspace*{\fill}
%\finalhyphendemerits=0
%[tba]}
%
%\index{Derby , West Lancashire@Derby, W. Lancs.}
%
%Death of David Swiffen (C).
%
%\noindent
%\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
%.
%\end{tabular*}

\subsection{Wyre}
\index{Wyre}

\subsubsection*{Tithebarn \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[7th October]}

\index{Tithebarn , Wyre@Tithebarn, \emph{Wyre}}

Death of Peter Hawley (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Lesley McKay & C & 847\\
Alan Morgan & Lab & 307\\
\end{tabular*}

\section{Leicestershire}

\subsection{Blaby}
\index{Blaby}

\subsubsection*{Saxondale \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[7th October]}

\index{Saxondale , Blaby@Saxondale, \emph{Blaby}}

Death of Alexandra Dilks (LD).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Christine Merrill & LD & 701\\
Nadina Kalsi & C & 311\\
Alan Methven & Lab & 243\\
Gary Reynolds & BNP & 94\\
\end{tabular*}

\subsubsection*{Blaby South \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[25th November]}

\index{Blaby South , Blaby@Blaby S., \emph{Blaby}}

Resignation of David Pollard (LD).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Antony Moseley & LD & 381\\
Marian Broomhead & C & 264\\
Inga Windley & Lab & 153\\
Peter Jarvis & BNP & 68\\
\end{tabular*}

\subsection{Charnwood}
\index{Charnwood}

\subsubsection*{Birstall Watermead \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[18th February]}

\index{Birstall Watermead , Charnwood@Birstall Watermead, \emph{Charnwood}}

Resignation of Rick Astill (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Iain Bentley & C & 674\\
Hayley Winrow & Lab & 452\\
Maurice Oatley & BNP & 288\\
\end{tabular*}

\subsection{Harborough}
\index{Harborough}

\subsubsection*{Market Harborough---Great Bowden and Arden \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[28th January; LD gain from C]}

\index{Market Harborough Great Bowden and Arden , Harborough@Market Harborough---Great Bowden \& Arden, \emph{Harborough}}

Resignation of Alistair Swatridge (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Phil Knowles & LD & 966\\
Barry Champion & C & 598\\
\end{tabular*}

\subsection{Leicester}
\index{Leicester}

EDP = English Democrats Party

\subsubsection*{Eyres Monsell \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Eyres Monsell , Leicester@Eyres Monsell, \emph{Leicester}}

Resignation of Kim Blower (Ind elected as Lab).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Virginia Cleaver & Lab & 1446\\
Jon Humberstone & C & 999\\
Scott Kennedy-Lount & LD & 908\\
Adrian Waudby & BNP & 745\\
\end{tabular*}

\subsubsection*{Castle \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[15th July; Lab gain from Grn]}

\index{Castle , Leicester@Castle, \emph{Leicester}}

Death of Phil Gordon (Grn).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Neil Clayton & Lab & 766\\
Mo Taylor & Grn & 625\\
Owen Jones & C & 411\\
Troy Lavers & LD & 150\\
Roy Rudham & EDP & 33\\
David Bowley & Ind & 11\\
Gareth Henry & Lib & 11\\
\end{tabular*}

\section{Lincolnshire}

\subsection{East Lindsey}
\index{East Lindsey}

\subsubsection*{North Holme \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[17th June; Lab gain from LD]}

\index{North Holme , East Lindsey@North Holme, \emph{E. Lindsey}}

Death of Clive Finch (LD).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Philip Sturman & Lab & 142\\
Fran Treanor & C & 111\\
Jez Boothman & BNP & 102\\
Mary Finch & LD & 88\\
Susan Locking & Ind & 72\\
\end{tabular*}

\subsection{Lincoln}
\index{Lincoln}

\subsubsection*{Moorland \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Moorland , Lincoln@Moorland, \emph{Lincoln}}

Resignation of Oliver Peake (C).

This by-election was combined with the 2010 ordinary election.
%; see page \pageref{MoorlandLincoln} for the result.

\subsection{North Kesteven}
\index{North Kesteven}

\subsubsection*{Branston \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Branston , North Kesteven@Branston, \emph{N. Kesteven}}

Death of Marjorie Duncan (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Raymond Cucksey & C & 1309\\
Peter Lundgren & Ind & 1202\\
Michael Clayton & BNP & 325\\
\end{tabular*}

\section{Norfolk}

%\subsection{County Council}
%
%\subsubsection*{Humbleyard \hspace*{\fill}\nolinebreak[1]%
%\enspace\hspace*{\fill}
%\finalhyphendemerits=0
%[13th January]}
%
%\index{Humbleyard , Norfolk@Humbleyard, Norfolk}
%
%Resignation of Daniel Cox (C).
%
%\noindent
%\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
%?
%\end{tabular*}

\subsection{Broadland}
\index{Broadland}

\subsubsection*{Taverham North \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[18th March; LD gain from C]}

\index{Taverham North , Broadland@Taverham N., \emph{Broadland}}

Resignation of Heath Dicks (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Nich Starling & LD & 630\\
John Griffin & C & 471\\
Jennifer Parkhouse & Grn & 54\\
\end{tabular*}

\subsection{Great Yarmouth}
\index{Great Yarmouth}

\subsubsection*{Claydon \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Claydon , Great Yarmouth@Claydon, \emph{Great Yarmouth}}

Death of Richard Barker (Lab).

This by-election was combined with the 2010 ordinary election.
%; see page \pageref{ClaydonGreatYarmouth} for the result.

\columnbreak

\subsection{King's Lynn and West Norfolk}
\index{King's Lynn and West Norfolk}

\subsubsection*{Mershe Lande \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May; C gain from Ind]}

\index{Mershe Lande , King's Lynn and West Norfolk@Mershe Lande, \emph{King's Lynn \& W. Norfolk}}

Resignation of David Markinson (Ind).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Jonathan Johns & C & 548\\
Carol Coleman & Ind & 372\\
John Nicholas-Letch & LD & 212\\
John Collop & Lab & 173\\
\end{tabular*}

\subsection{North Norfolk}
\index{North Norfolk}

\subsubsection*{Lancaster South \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Lancaster South , North Norfolk@Lancaster S., \emph{N. Norfolk}}

Resignation of Stephanie Towers (LD).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
John Lisher & LD & 1066\\
Thomas Fitzpatrick & C & 784\\
Monika Wiedmann & Grn & 122\\
\end{tabular*}

\subsection{Norwich}
\index{Norwich}

For the results of the thirteen by-elections held on 9th September, following the disqualification of the councillors elected in 2006 after the High Court ruled that their terms had expired, see
\url{https://www.andrewteale.me.uk/u279}.
%pages \pageref{NorwichStart} to \pageref{NorwichEnd}.

\section{Northamptonshire}

\subsection{Daventry}
\index{Daventry}

\subsubsection*{Abbey North \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Abbey North , Daventry@Abbey N., \emph{Daventry}}

Resignation of Barry Howard (C).

This by-election was combined with the 2010 ordinary election.
%; see page \pageref{AbbeyNorthDaventry} for the result.

\subsection{Wellingborough}
\index{Wellingborough}

EDP = English Democrats Party

\subsubsection*{Redwell West \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[11th March]}

\index{Redwell West , Wellingborough@Redwell W., \emph{Wellingborough}}

Resignation of Andrew Bigley (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
John Raymond & C & 570\\
Graham Sherwood & Lab & 169\\
David Robinson & BNP & 84\\
Penelope Wilkins & LD & 72\\
Terence Spencer & EDP & 62\\
Jonathan Hornett & Grn & 23\\
\end{tabular*}

\subsubsection*{Earls Barton \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[17th June; C gain from Ind]}

\index{Earls Barton , Wellingborough@Earls Barton, \emph{Wellingborough}}

Disqualification (non-attendance) of Lucy Payne (Ind).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Andrew Atkinson & C & 639\\
Peter Wright & Lab & 425\\
Daniel Jones & LD & 229\\
Jonathan Hornett & Grn & 38\\
\end{tabular*}

\section{Northumberland}
\index{Northumberland}

\subsubsection*{Ponteland East \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[4th November]}

\index{Ponteland East , Northumberland@Ponteland E., \emph{Northd.}}

Death of Mel Armstrong (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Eileen Armstrong & C & 843\\
Andrew Duffield & LD & 403\\
Andrew Avery & Lab & 100\\
\end{tabular*}

\section{North Yorkshire}

\subsection{Harrogate}
\index{Harrogate}

\subsubsection*{Woodfield \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[7th January]}

\index{Woodfield , Harrogate@Woodfield, \emph{Harrogate}}

Death of John Wren (C elected as LD).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Greta Knight & LD & 688\\
Heather Adderley & C & 246\\
Steven Gill & BNP & 92\\
Daniel Maguire & Lab & 73\\
\end{tabular*}

\subsection{Middlesbrough}
\index{Middlesbrough}

\subsubsection*{Ayresome \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[9th September; Ind gain from Lab]}

\index{Ayresome , Middlesbrough@Ayresome, \emph{Middlesbrough}}

Resignation of Barbara Dunne (Lab).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
William Hawthorne & Ind & 456\\
Stephen Cass & Lab & 414\\
James Ruddock & C & 73\\
\end{tabular*}

\subsection{Redcar and Cleveland}
\index{Redcar and Cleveland}

\subsubsection*{Brotton \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[26th August]}

\index{Brotton , Redcar and Cleveland@Brotton, \emph{Redcar \& Cleveland}}

Resignation of Peter Scott (Lab).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Doreen Rudland & Lab & 565\\
Barry Hunt & Ind & 351\\
Val Miller & LD & 315\\
Donald Agar & C & 220\\
Michael George & BNP & 33\\
\end{tabular*}

\subsection{Ryedale}
\index{Ryedale}

\subsubsection*{Norton West \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May; LD gain from Ind]}

\index{Norton West , Ryedale@Norton W., \emph{Ryedale}}

Death of David Jackson (Ind).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Hugh Spencer & LD & 579\\
Judith Denniss & C & 455\\
Trevor Moss & BNP & 107\\
\end{tabular*}

\subsection{Scarborough}
\index{Scarborough}

\subsubsection*{Mayfield \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[11th February]}

\index{Mayfield , Scarborough@Mayfield, \emph{Scarborough}}

Death of Peter Booth (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Steven Leadley & C & 436\\
Derek Robinson & Ind & 282\\
Janet Peake & Lab & 238\\
Bill Miller & Ind & 112\\
Christopher Cawood & LD & 65\\
\end{tabular*}

\columnbreak

\subsubsection*{Eastfield \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[Friday 24th September]}

\index{Eastfield , Scarborough@Eastfield, \emph{Scarborough}}

Death of Brian O'Flynn (LD).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Johan Zegstroo & LD & 182\\
John Warburton & Lab & 159\\
Nicholas Butterworth & Ind & 110\\
Carl Morris & C & 100\\
Trisha Scott & BNP & 27\\
Michael Cutler & Grn & 13\\
\end{tabular*}

\subsection{York}
\index{York}

\subsubsection*{Hull Road \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[14th October]}

\index{Hull Road , York@Hull Rd., \emph{York}}

Resignation of Roger Pierce (Lab).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Mick Hoban & Lab & 860\\
Robin Dickson & C & 296\\
Rachel Williams & LD & 183\\
John Cossham & Grn & 84\\
Trevor Brown & BNP & 42\\
\end{tabular*}

\section{Nottinghamshire}

MIF = Mansfield Independent Forum

\subsection{County Council}
\index{Nottinghamshire}

\subsubsection*{Mansfield South \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[25th February; Lab gain from MIF]}

\index{Mansfield South , Nottinghamshire@Mansfield S., \emph{Notts.}}

Death of Tom Appleby (MIF).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Chris Winterton & Lab & 1342\\
Andrew Tristram & MIF & 1108\\
Drew Stafford & C & 774\\
Nick Bennett & UKIP & 489\\
Danielle Gent & LD & 295\\
\end{tabular*}

\subsubsection*{Worksop West \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[16th September; Lab gain from C]}

\index{Worksop West , Nottinghamshire@Worksop W., \emph{Notts.}}

Death of Michael Bennett (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Kevin Greaves & Lab & 1457\\
Alec Thorpe & C & 755\\
Leon Duveen & LD & 88\\
Ronald Dawes & Ind & 56\\
Terry Coleman & Ind & 13\\
\end{tabular*}

\subsection{Ashfield}
\index{Ashfield}

\subsubsection*{Hucknall Central \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[11th February; Lab gain from C]}

\index{Hucknall Central , Ashfield@Hucknall C., \emph{Ashfield}}

Death of Gordon Riley (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Trevor Locke & Lab & 675\\
Mick Murphy & C & 437\\
Ken Cotham & LD & 357\\
Ron Nixon & UKIP & 158\\
Edward Holmes & BNP & 131\\
\end{tabular*}

\subsection{Bassetlaw}
\index{Bassetlaw}

At the May 2010 ordinary election there was an unfilled vacancy in Worksop North ward due to the resignation of Steven Burton (C).
\index{Worksop North , Bassetlaw@Worksop N., \emph{Bassetlaw}}

%There was an unfilled vacancy in Worksop North ward at the ordinary May elections following the resignation of Steven Burton (C) with less than six months of his term remaining.

\subsubsection*{Worksop South \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[16th September; Lab gain from C]}

\index{Worksop South , Bassetlaw@Worksop S., \emph{Bassetlaw}}

Death of Michael Bennett (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Sylvia May & Lab & 815\\
Alex Thorpe & C & 669\\
Leon Duveen & LD & 84\\
\end{tabular*}

\subsubsection*{Harworth \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[21st October]}

\index{Harworth , Bassetlaw@Harworth, \emph{Bassetlaw}}

Resignation of John Clayton (Lab).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Gloria Evans & Lab & 1345\\
Tracey Taylor & C & 182\\
Richard Bennett & Ind & 68\\
Mark Hunter & LD & 39\\
\end{tabular*}

\subsection{Broxtowe}
\index{Broxtowe}

\subsubsection*{Eastwood South \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[25th February; LD gain from Lab]}

\index{Eastwood South , Broxtowe@Eastwood S., \emph{Broxtowe}}

Death of Jim Kenny (Lab).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Keith Longdon & LD & 985\\
Ken Woodhead & Lab & 484\\
Adrian Limb & C & 387\\
\end{tabular*}

\subsubsection*{Cossall and Kimberley \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[19th August]}

\index{Cossall and Kimberley , Broxtowe@Cossall \& Kimberley, \emph{Broxtowe}}

Disqualification (non-attendance) of Tony Rutherford (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Shane Easom & C & 757\\
Mary McGuckin & Lab & 731\\
Elaine Cockburn & LD & 524\\
\end{tabular*}

\subsection{Mansfield}
\index{Mansfield}

\subsubsection*{Portland \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[25th February; Lab gain from MIF]}

\index{Portland , Mansfield@Portland, \emph{Mansfield}}

Death of Tom Appleby (MIF).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Brian Lohan & Lab & 407\\
Deirdre Appleby & MIF & 263\\
Fraser McFarland & C & 116\\
Nicholas Spencer & LD & 66\\
Philip Smith & UKIP & 37\\
\end{tabular*}

\subsubsection*{Sherwood \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[25th February; Lab gain from MIF]}

\index{Sherwood , Mansfield@Sherwood, \emph{Mansfield}}

Death of Norman Cook (MIF).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Julia Yemm & Lab & 406\\
Eric Milnes & MIF & 171\\
Brian Hyatt & C & 156\\
Andrew Hamilton & UKIP & 93\\
Anna Ellis & LD & 49\\
\end{tabular*}

\subsection{Newark and Sherwood}
\index{Newark and Sherwood}

\subsubsection*{Rainworth \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[1st July]}

\index{Rainworth , Newark and Sherwood@Rainworth, \emph{Newark \& Sherwood}}

Death of Allen Tift (Lab).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Linda Tift & Lab & 735\\
Mike Warner & C & 219\\
Alan Armin & Ind & 144\\
\end{tabular*}

\subsection{Rushcliffe}
\index{Rushcliffe}

\subsubsection*{Wiverton \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May; C gain from Ind]}

\index{Wiverton , Rushcliffe@Wiverton, \emph{Rushcliffe}}

Resignation of David Barlow (Ind).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Sarah Bailey & C & 1264\\
Sue Hull & LD & 1076\\
\end{tabular*}

\section{Oxfordshire}

\subsection{Cherwell}
\index{Cherwell}

\subsubsection*{Kidlington North \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[22nd July]}

\index{Kidlington North , Cherwell@Kidlington N., \emph{Cherwell}}

Death of John Wyse (LD).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Alaric Rose & LD & 526\\
Eddie Stevens & C & 419\\
Catherine Arakelian & Lab & 216\\
David Fairweather & UKIP & 86\\
\end{tabular*}

\subsection{Oxford}
\index{Oxford}

\subsubsection*{Barton and Sandhills \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[21st October; Lab gain from LD]}

\index{Barton and Sandhills , Oxford@Barton \& Sandhills, \emph{Oxford}}

Resignation of Patrick Murray (LD).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Michael Rowley & Lab & 837\\
Hugh Baylis & LD & 334\\
Mary-Jane Sareva & Grn & 119\\
Siddharth Deva & C & 86\\
Julia Gasper & UKIP & 48\\
Michael McAndrews & Ind & 42\\
\end{tabular*}

\subsection{South Oxfordshire}
\index{South Oxfordshire}

Henley = Henley Residents Group

\subsubsection*{Henley South \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[11th February]}

\index{Henley South , South Oxfordshire@Henley S., \emph{S. Oxon.}}

Death of Terry Buckett (Henley).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Elizabeth Hodgkin & Henley & 642\\
David Silvester & C & 472\\
George Levy & LD & 110\\
\end{tabular*}

\subsubsection*{Crowmarsh \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[3rd June; LD gain from C]}

\index{Crowmarsh , South Oxfordshire@Crowmarsh, \emph{S. Oxon.}}

Death of Nicholas Odd (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
John Griffin & LD & 327\\
Kristina Crabbe & C & 258\\
\end{tabular*}

\subsection{West Oxfordshire}
\index{West Oxfordshire}

At the May 2010 ordinary election there was an unfilled vacancy in Carterton North West ward due to the death of Dave King (C).
\index{Carterton North West , West Oxfordshire@Carterton N.W., \emph{W. Oxon.}}

%There was an unfilled vacancy in Carterton North West ward at the ordinary May elections following the death of Dave King (C) with less than six months of his term remaining.

\section{Shropshire}

\subsection{Shropshire}
\index{Shropshire}

\subsubsection*{Clee \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[1st July]}

\index{Clee , Shropshire@Clee, \emph{Shrops.}}

Resignation of Paul Andrews (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Richard Huffer & LD & 946\\
Hayley Fernihough & C & 506\\
Graeme Perks & Ind & 116\\
\end{tabular*}

\subsection{Telford and Wrekin}
\index{Telford and Wrekin}

TWPA = Telford and Wrekin Peoples Alliance

\subsubsection*{College \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[11th February; C gain from Ind]}

\index{College , Telford and Wrekin@College, \emph{Telford \& Wrekin}}

Resignation of Gary Davies (Ind).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
David Chaplin & C & 252\\
Patrick McCarthy & Ind & 237\\
Michael Ion & Lab & 219\\
Nusrat Janjua & Ind & 127\\
Richard Choudhary & TWPA & 24\\
\end{tabular*}

\subsubsection*{The Nedge \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[11th February; C gain from Lab]}

\index{Nedge , Telford and Wrekin@The Nedge, \emph{Telford \& Wrekin}}

Death of Ute Sambrook (Lab).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Harvey Unwin & C & 760\\
Shaun Davies & Lab & 688\\
Ray Knight & UKIP & 237\\
Terence Gould & BNP & 103\\
\end{tabular*}

\section{Somerset}

\subsection{Bath and North East Somerset}
\index{Bath and North East Somerset}

\subsubsection*{Radstock \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[29th July; LD gain from Ind]}

\index{Radstock , Bath and North East Somerset@Radstock, \emph{Bath \& N.E. Somerset}}

Death of Allan Hall (Ind).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Simon Allen & LD & 542\\
Lesley Mansell & Lab & 386\\
Keith Pate & Ind & 370\\
Deirdre Horstmann & C & 55\\
\end{tabular*}

\subsection{Mendip}
\index{Mendip}

\subsubsection*{Shepton West \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[1st July; LD gain from C]}

\index{Shepton West , Mendip@Shepton W., \emph{Mendip}}

Disqualification (non-attendance) of Ashley Taylor (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Garfield Kennedy & LD & 459\\
Judy Bartlett & C & 358\\
Chris Inchley & Lab & 241\\
Chris Briton & Grn & 44\\
\end{tabular*}

\subsubsection*{Ashwick, Chilcompton and Stratton \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[21st October]}

\index{Ashwick, Chilcompton and Stratton , Mendip@Ashwick, Chilcompton \& Stratton, \emph{Mendip}}

Resignation of Maxine Oxford (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Steven Priscott & C & 491\\
Tom Buckley & LD & 440\\
Roger Anderson & Lab & 111\\
Chris Briton & Grn & 46\\
\end{tabular*}

\subsection{Sedgemoor}
\index{Sedgemoor}

\subsubsection*{Woolavington \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[30th September; C gain from Lab]}

\index{Woolavington , Sedgemoor@Woolavington, \emph{Sedgemoor}}

Death of Roger Lavers (Lab).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Alison Hamlin & C & 264\\
Tina Marsh & LD & 184\\
Ian Tucker & Lab & 141\\
\end{tabular*}

\subsection{South Somerset}
\index{South Somerset}

\subsubsection*{Tower \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Tower , South Somerset@Tower, \emph{S. Somerset}}

Resignation of Maili Felton (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Michael Beech & C & 962\\
Gordon Czaprewski & LD & 620\\
\end{tabular*}

\subsection{Taunton Deane}
\index{Taunton Deane}

\subsubsection*{Lyngford \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[28th January]}

\index{Lyngford , Taunton Deane@Lyngford, \emph{Taunton Deane}}

Disqualification (non-attendance) of Julie Wood (LD).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Ben Swaine & LD & 390\\
John Gage & C & 253\\
Martin Jevon & Lab & 190\\
Charlene Sherriff & UKIP & 59\\
\end{tabular*}

\section{Staffordshire}

\subsection{Cannock Chase}
\index{Cannock Chase}

\subsubsection*{Heath Hayes East and Wimblebury \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[26th August; Lab gain from C]}

\index{Heath Hayes East and Wimblebury , Cannock Chase@Heath Hayes E. \& Wimblebury, \emph{Cannock Chase}}

Death of John Jillings (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Diane Todd & Lab & 418\\
Lisa Pearce & C & 238\\
Andrew Clark & LD & 153\\
Ron Turville & Ind & 30\\
\end{tabular*}

\subsection{East Staffordshire}
\index{East Staffordshire}

\subsubsection*{Bagots \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Bagots , East Staffordshire@Bagots, \emph{E. Staffs.}}

Resignation of Alex Fox (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Greg Hall & C & 1177\\
Charles Dean-Young & LD & 414\\
\end{tabular*}

\subsubsection*{Abbey \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[21st October]}

\index{Abbey , East Staffordshire@Abbey, \emph{E. Staffs.}}

Resignation of Kathy Lamb (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Colin Whittaker & C & 604\\
Liz Harman & Lab & 84\\
\end{tabular*}

\subsection{Newcastle-under-Lyme}
\index{Newcastle-under-Lyme}

\subsubsection*{Newchapel \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[4th February]}

\index{Newchapel , Newcastle-under-Lyme@Newchapel, \emph{Newcastle-under-Lyme}}

Death of Nora Salt (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Susan Short & C & 208\\
Carol Lovatt & UKIP & 148\\
Kyle Robinson & Lab & 138\\
Adrian Rhodes & LD & 127\\
\end{tabular*}

\subsubsection*{Westlands \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Westlands , Newcastle-under-Lyme@Westlands, \emph{Newcastle-under-Lyme}}

Resignation of Mary Moss (C).

This by-election was combined with the 2010 ordinary election.
%; see page \pageref{WestlandsNewcastleLyme} for the result.

\subsection{South Staffordshire}
\index{South Staffordshire}

\subsubsection*{Huntington and Hatherton \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[1st July]}

\index{Huntington and Hatherton , South Staffordshire@Huntington \& Hatherton, \emph{S. Staffs.}}

Death of Patricia Williams (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
David Williams & C & 237\\
Ron Kenyon & Lab & 235\\
David Percox & Ind & 64\\
\end{tabular*}

\subsection{Stafford}
\index{Stafford}

\subsubsection*{Gnosall and Woodseaves \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Gnosall and Woodseaves , Stafford@Gnosall \& Woodseaves, \emph{Stafford}}

Death of James Kelly (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Ann Kelly & C & 2336\\
David Kirby & LD & 1240\\
John Gale & Grn & 255\\
\end{tabular*}

\subsection{Stoke-on-Trent}
\index{Stoke-on-Trent}

At the May 2010 ordinary election there was an unfilled vacancy in Blurton ward due to the death of Derek Hall (City Independent).
\index{Blurton , Stoke-on-Trent@Blurton, \emph{Stoke-on-Trent}}

%There was an unfilled vacancy in Blurton ward at the ordinary May elections following the death of Derek Hall (City Independent) with less than six months of his term remaining.

\section{Suffolk}

\subsection{County Council}
\index{Suffolk}

\subsubsection*{Aldeburgh and Leiston \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Aldeburgh and Leiston , Suffolk@Aldeburgh \& Leiston, \emph{Suffolk}}

Resignation of Ron Ward (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Richard Smith & C & 2240\\
Joan Girling & Ind & 1439\\
Terry Hodgson & Lab & 1243\\
\end{tabular*}

\subsubsection*{Tower \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[11th November]}

\index{Tower , Suffolk@Tower, \emph{Suffolk}}

Resignation of Paul Farmer (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Stefan Oliver & C & 1005\\
David Nettleton & Ind & 950\\
Kevin Hind & Lab & 759\\
Pippa Judd & Grn & 479\\
David Chappell & LD & 300\\
\end{tabular*}

\subsection{Babergh}
\index{Babergh}

\subsubsection*{Great Cornard North \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[22nd July; Lab gain from C]}

\index{Great Cornard North , Babergh@Great Cornard N., \emph{Babergh}}

Resignation of Carole Todd (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Anthony Bavington & Lab & 340\\
Martin Fryer & C & 201\\
Richard Platt & LD & 141\\
Leon Stedman & UKIP & 72\\
\end{tabular*}

\subsection{Ipswich}
\index{Ipswich}

\subsubsection*{Alexandra \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Alexandra , Ipswich@Alexandra, \emph{Ipswich}}

Resignation of Louise Gooch (LD).

This by-election was combined with the 2010 ordinary election.
%; see page \pageref{AlexandraIpswich} for the result.

\subsection{Mid Suffolk}
\index{Mid Suffolk}

\subsubsection*{Haughley and Wetherden \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[25th March; Grn gain from C]}

\index{Haughley and Wetherden , Mid Suffolk@Haughley \& Wetherden, \emph{Mid Suffolk}}

Resignation of Bruce Cameron-Laker (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Rachel Eburne & Grn & 444\\
Samantha Powell & C & 176\\
Chris Vecchi & LD & 51\\
David Hill & Lab & 32\\
Christopher Streatfield & UKIP & 25\\
\end{tabular*}

%\subsection{Waveney}
%
%\subsubsection*{Southwold and Reydon \hspace*{\fill}\nolinebreak[1]%
%\enspace\hspace*{\fill}
%\finalhyphendemerits=0
%[tba]}
%
%\index{Southwold and Reydon , Waveney@Southwold \& Reydon, Waveney}
%
%Resignation of Simon Tobin (C).
%
%\noindent
%\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
%?
%\end{tabular*}
%
\section{Surrey}

\subsection{County Council}
\index{Surrey}

Peace = Peace Party

\subsubsection*{Walton South and Oatlands \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Walton South and Oatlands , Surrey@Walton S. \& Oatlands, \emph{Surrey}}

Resignation of Roy Taylor (LD).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Anthony Samuels & C & 5231\\
Vicki MacLeod & LD & 2802\\
\end{tabular*}

\subsubsection*{Worplesdon \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[15th July]}

\index{Worplesdon , Surrey@Worplesdon, \emph{Surrey}}

Death of Mike Nevins (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Nigel Sutcliffe & C & 1844\\
Paul Cragg & LD & 1286\\
Martin Phillips & Lab & 193\\
Mazhar Manzoor & UKIP & 78\\
John Morris & Peace & 39\\
\end{tabular*}

\subsection{Elmbridge}
\index{Elmbridge}

StGHI = St George's Hill Independents

\subsubsection*{Hersham South \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Hersham South , Elmbridge@Hersham S., \emph{Elmbridge}}

Resignation of Lara Conaway (C).

This by-election was combined with the 2010 ordinary election.
%; see page \pageref{HershamSElmbridge} for the result.

\subsubsection*{Hersham North \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[21st October]}

\index{Hersham North , Elmbridge@Hersham N., \emph{Elmbridge}}

Resignation of Doug Packer (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Simon Desborough & C & 463\\
Roy Green & Ind & 453\\
Peter Jepson & Lab & 135\\
\end{tabular*}

\subsubsection*{St George's Hill \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[21st October]}

\index{Saint George's Hill , Elmbridge@St George's Hill, \emph{Elmbridge}}

Death of John Bartlett (StGHI).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Peter Harman & StGHI & 515\\
Melissa Lake & C & 412\\
Robert Evans & Lab & 36\\
\end{tabular*}

\subsection{Guildford}
\index{Guildford}

\subsubsection*{Pirbright \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[15th July]}

\index{Pirbright , Guildford@Pirbright, \emph{Guildford}}

Death of Mike Nevins (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Gordon Jackson & C & 364\\
Philip Douetil & LD & 199\\
\end{tabular*}

\subsection{Mole Valley}
\index{Mole Valley}

\subsubsection*{Capel, Leigh and Newdigate \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[21st October; LD gain from C]}

\index{Capel, Leigh and Newdigate , Mole Valley@Capel, Leigh \& Newdigate, \emph{Mole Valley}}

Resignation of Philip Warren (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.575\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Iain Murdoch & LD & 618\\
\sloppyword{Corinna Osborne-Patterson} & C & 558\\
Tim Bowling & UKIP & 97\\
Jacqui Hamlin & Grn & 61\\
\end{tabular*}

\subsection{Reigate and Banstead}
\index{Reigate and Banstead}

\subsubsection*{Redhill East (2) \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Redhill East , Reigate and Banstead@Redhill E., \emph{Reigate \& Banstead}}

Death of Frank Moore and resignation of Daniel Poulter (both C).

This double by-election was combined with the 2010 ordinary election.
%; see page \pageref{RedhillEReigateBanstead} for the result.

\subsection{Tandridge}
\index{Tandridge}

\subsubsection*{Whyteleafe \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[Tuesday 2nd February]}

\index{Whyteleafe , Tandridge@Whyteleafe, \emph{Tandridge}}

Resignation of Jeffrey Gray (LD).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
David Lee & LD & 444\\
Chris Krishnan & C & 236\\
Jeffrey Bolter & UKIP & 99\\
\end{tabular*}

\subsection{Woking}
\index{Woking}

\subsubsection*{Byfleet \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Byfleet , Woking@Byfleet, \emph{Woking}}

Resignation of Simon Hutton (C).

This by-election was combined with the 2010 ordinary election.
%; see page \pageref{ByfleetWoking} for the result.

\section{Warwickshire}

\subsection{County Council}
\index{Warwickshire}

\subsubsection*{Nuneaton St Nicholas \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Nuneaton Saint Nicholas , Warwickshire@Nuneaton St Nicholas, \emph{Warks.}}

Death of David Bryden (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Jeffrey Clarke & C & 3195\\
Paul Hickling & Lab & 1616\\
Keith Kondakor & Grn & 589\\
Thomas Wilson & Ind & 280\\
\end{tabular*}

\subsubsection*{Studley \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Studley , Warwickshire@Studley, \emph{Warks.}}

Resignation of Martin Barry (LD).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Clive Rickhards & LD & 1906\\
Justin Kerridge & C & 1755\\
Jacqueline Abbott & Lab & 480\\
Karen Varga & Grn & 128\\
\end{tabular*}

\subsection{Nuneaton and Bedworth}
\index{Nuneaton and Bedworth}

At the May 2010 ordinary election there was an unfilled vacancy in St Nicholas ward due to the death of David Bryden (C).
\index{Saint Nicholas , Nuneaton and Bedworth@St Nicholas, \emph{Nuneaton \& Bedworth}}

%There was an unfilled vacancy in St Nicholas ward at the ordinary May elections following the death of David Bryden (C) with less than six months of his term remaining.

\subsection{Rugby}
\index{Rugby}

At the May 2010 ordinary election there was an unfilled vacancy in Dunchurch and Knightlow ward due to the death of Ron Ravenhall (LD).
\index{Dunchurch and Knightlow , Rugby@Dunchurch \& Knightlow, \emph{Rugby}}
%There was an unfilled vacancy in Dunchurch and Knightlow ward at the ordinary May elections following the death of Ron Ravenhall (LD) with less than six months of his term remaining.

\subsubsection*{Dunchurch and Knightlow \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[2nd December]}

\index{Dunchurch and Knightlow , Rugby@Dunchurch \& Knightlow, \emph{Rugby}}

Resignation of Mike Galsworthy (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Ian Lowe & C & 832\\
Robert Aird & LD & 682\\
Robert McNally & Lab & 149\\
George Hougez & Grn & 20\\
\end{tabular*}

\subsection{Stratford-on-Avon}
\index{Stratford-on-Avon}

\subsubsection*{Henley \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Henley , Stratford-on-Avon@Henley, \emph{Stratford-on-Avon}}

Resignation of Laurence Marshall (C).

This by-election was combined with the 2010 ordinary election.
%; see page \pageref{HenleyArdenStratfordAvon} for the result.

\subsubsection*{Shipston \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Shipston , Stratford-on-Avon@Shipston, \emph{Stratford-on-Avon}}

Resignation of Bob White (LD).

This by-election was combined with the 2010 ordinary election.
%; see page \pageref{ShipstonStratfordAvon} for the result.

\subsection{Warwick}
\index{Warwick}

\subsubsection*{Warwick South \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[22nd July]}

\index{Warwick South , Warwick@Warwick S., \emph{Warwick}}

Resignation of Chris White (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Linda Bromley & C & 1107\\
Chris McKeown & Lab & 648\\
Chris Spedding & LD & 294\\
\end{tabular*}

\section{West Sussex}

Justice = Justice Party

\subsection{County Council}
\index{West Sussex}

\subsubsection*{East Grinstead South and Ashurst Wood \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{East Grinstead South and Ashurst Wood , West Sussex@East Grinstead S. \& Ashurst Wood, \emph{W. Sussex}}

Resignation of Lee Quinn (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
John O'Brien & C & 2878\\
Catrin Ingham & LD & 2771\\
Robert Wall & Ind & 328\\
\end{tabular*}

\subsubsection*{Maidenbower \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[7th October]}

\index{Maidenbower , West Sussex@Maidenbower, \emph{W. Sussex}}

Resignation of Henry Smith (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Robert Lanzer & C & 1036\\
Peter Smith & Lab & 417\\
Sulu Pandya & LD & 82\\
John Mac Canna & UKIP & 61\\
Arshad Khan & Justice & 12\\
\end{tabular*}

\subsection{Adur}
\index{Adur}

\subsubsection*{Eastbrook \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Eastbrook , Adur@Eastbrook, \emph{Adur}}

Resignation of Emma Evans (C).

This by-election was combined with the 2010 ordinary election.
%; see page \pageref{EastbrookAdur} for the result.

\subsection{Chichester}
\index{Chichester}

\subsubsection*{Plaistow \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[11th February]}

\index{Plaistow , Chichester@Plaistow, \emph{Chichester}}

Resignation of Brian Hooton (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Philippa Hardwick & C & 504\\
Raymond Cooper & LD & 301\\
Andrew Emerson & BNP & 69\\
\end{tabular*}

\subsubsection*{Rogate \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[17th June]}

\index{Rogate , Chichester@Rogate, \emph{Chichester}}

Resignation of William Mason (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Nigel Johnson-Hill & C & \emph{unop.}\\
\end{tabular*}

\subsubsection*{Plaistow \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[25th November]}

\index{Plaistow , Chichester@Plaistow, \emph{Chichester}}

Resignation of John Andrews (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Linda Westmore & C & 416\\
Ray Cooper & LD & 289\\
Gail Weingartner & UKIP & 62\\
\end{tabular*}

\subsection{Crawley}
\index{Crawley}

\subsubsection*{Tilgate \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[7th October; Lab gain from C]}

\index{Tilgate , Crawley@Tilgate, \emph{Crawley}}

Resignation of Lawrence Taylor (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Colin Lloyd & Lab & 764\\
Ray Ward & C & 656\\
Maurice Day & UKIP & 79\\
Arshad Khan & Justice & 6\\
\end{tabular*}

\subsection{Mid Sussex}
\index{Mid Sussex}

\subsubsection*{Cuckfield \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Cuckfield , Mid Sussex@Cuckfield, \emph{Mid Sussex}}

Death of Brenda Binge (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Robert Salisbury & C & 1597\\
Stephen Blanch & LD & 1362\\
\end{tabular*}

\subsubsection*{Haywards Heath Heath \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May; LD gain from C]}

\index{Haywards Heath Heath , Mid Sussex@Haywards Heath Heath, \emph{Mid Sussex}}

Resignation of Margaret Baker (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Sue Ng & LD & 1350\\
Ruth de Mierre & C & 1310\\
Alan Yates & Lab & 221\\
\end{tabular*}

\subsubsection*{High Weald \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{High Weald , Mid Sussex@High Weald, \emph{Mid Sussex}}

Resignation of James Temple-Smithson (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Simon McMenemy & C & 1670\\
Anne-Marie Lucraft & LD & 922\\
Paul Brown & Grn & 395\\
\end{tabular*}

\subsubsection*{Hurstpierpoint and Downs \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Hurstpierpoint and Downs , Mid Sussex@Hurstpierpoint \& Downs, \emph{Mid Sussex}}

Resignation of Christopher Maidment (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Anna Deflippo & C & 2362\\
Rodney Jackson & LD & 1848\\
\end{tabular*}

\subsubsection*{Haywards Heath Franklands \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[29th July]}

\index{Haywards Heath Franklands , Mid Sussex@Haywards Heath Franklands, \emph{Mid Sussex}}

Death of Clive Chapman (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
John de Mierre & C & 545\\
Raha Kazemi & LD & 464\\
Colin Bates & Ind & 63\\
\end{tabular*}

\subsection{Worthing}
\index{Worthing}

At the May 2010 ordinary election there was an unfilled vacancy in Salvington ward due to the resignation of Heather Mercer (C).
\index{Salvington , Worthing@Salvington, \emph{Worthing}}

%There was an unfilled vacancy in Salvington ward at the ordinary May elections following the resignation of Heather Mercer (C) with less than six months of her term remaining.

\subsubsection*{Marine \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Marine , Worthing@Marine, \emph{Worthing}}

Resignation of Keith Mercer (C).

This by-election was combined with the 2010 ordinary election.
%; see page \pageref{MarineWorthing} for the result.

\section{Wiltshire}

\subsection{Swindon}
\index{Swindon}

\subsubsection*{Moredon \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[4th November; Lab gain from C]}

\index{Moredon , Swindon@Moredon, \emph{Swindon}}

Resignation of Steph Exell (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Jenny Millin & Lab & 887\\
Toby Elliott & C & 755\\
William Oram & UKIP & 129\\
Chris Ward & LD & 98\\
\end{tabular*}

\subsection{Wiltshire}
\index{Wiltshire}

\subsubsection*{Bromham, Rowde and Potterne \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[Tuesday 21st December]}

\index{Bromham, Rowde and Potterne , Wiltshire@Bromham, Rowde \& Potterne, \emph{Wilts.}}

Resignation of Philip Brown (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Liz Bryant & C & 561\\
Paul Mortimer & LD & 358\\
Andrew Jones & Lab & 74\\
Pat Bryant & Ind & 55\\
\end{tabular*}

\section{Worcestershire}

\subsection{County Council}
\index{Worcestershire}

\subsubsection*{Bowbrook \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[25th November]}

\index{Bowbrook , Worcestershire@Bowbrook, \emph{Worcs.}}

Death of Ted Sheldon (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Tony Miller & C & 1088\\
Margaret Rowley & LD & 536\\
Chris Barton & Lab & 213\\
\end{tabular*}

\subsubsection*{Alvechurch \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[16th December]}

\index{Alvechurch , Worcestershire@Alvechurch, \emph{Worcs.}}

Resignation of George Lord (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
June Griffiths & C & 637\\
Christopher Bloore & Lab & 189\\
Dee Morton & Ind & 157\\
Howard Allen & LD & 83\\
Kenneth Wheatley & Ind & 79\\
Steven Morson & UKIP & 65\\
\end{tabular*}

\subsection{Bromsgrove}
\index{Bromsgrove}

\subsubsection*{Marlbrook \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[16th December]}

\index{Marlbrook , Bromsgrove@Marlbrook, \emph{Bromsgrove}}

Resignation of George Lord (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
John Ruck & C & 284\\
Martin Knight & Lab & 236\\
Charlie Bateman & Ind & 138\\
Steven Morson & UKIP & 68\\
Janet King & LD & 67\\
Peter Harvey & Grn & 14\\
Kenneth Wheatley & Ind & 4\\
\end{tabular*}

\subsection{Redditch}
\index{Redditch}

\subsubsection*{Crabbs Cross \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Crabbs Cross , Redditch@Crabbs Cross, \emph{Redditch}}

Death of Jack Field (C).

This by-election was combined with the 2010 ordinary election.
%; see page \pageref{CrabbsXRedditch} for the result.

\subsection{Worcester}
\index{Worcester}

At the May 2010 ordinary election there was an unfilled vacancy in Bedwardine ward due to the death of Barry Mackenzie-Williams (C).
\index{Bedwardine , Worcester@Bedwardine, \emph{Worcester}}

%There was an unfilled vacancy in Bedwardine ward at the ordinary May elections following the death of Barry Mackenzie-Williams (C) with less than six months of his term remaining.

\subsection{Wychavon}
\index{Wychavon}

\subsubsection*{Evesham South \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[18th February]}

\index{Evesham South , Wychavon@Evesham S., \emph{Wychavon}}

Death of Ron Cartwright (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Gerry O'Donnell & C & 358\\
Diana Brown & LD & 176\\
John White & UKIP & 150\\
\end{tabular*}

\section{Glamorgan}

\subsection{Bridgend}
\index{Bridgend}

\subsubsection*{Pendre \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[18th February; Lab gain from LD]}

\index{Pendre , Bridgend@Pendre, \emph{Bridgend}}

Resignation of Mike Simmonds (LD).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Richard Young & Lab & 200\\
Anita Davies & LD & 193\\
Diane Armstrong & Ind & 68\\
Alan Wathan & C & 60\\
Tim Thomas & PC & 25\\
\end{tabular*}

\subsection{Neath Port Talbot}
\index{Neath Port Talbot}

NPTIP = Neath Port Talbot Independent Party

\subsubsection*{Neath North \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Neath North , Neath Port Talbot@Neath N., \emph{Neath Port Talbot}}

Resignation of Derek Vaughan MEP (Lab).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Alan Lockyer & Lab & 923\\
Breandan MacCathail & PC & 305\\
Brian Warlow & Ind & 296\\
Tony Phillips & NPTIP & 239\\
Stephen Carpenter & C & 208\\
\end{tabular*}

\subsubsection*{Neath North \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[14th October]}

\index{Neath North , Neath Port Talbot@Neath N., \emph{Neath Port Talbot}}

Death of Mannie Loaring (Lab).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Mark Protheroe & Lab & 437\\
David Howells & NPTIP & 144\\
Breandan MacCathail & PC & 132\\
Mathew McCarthy & LD & 51\\
\end{tabular*}

\subsection{Rhondda Cynon Taf}
\index{Rhondda Cynon Taf}

\subsubsection*{Cymmer \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[22nd July]}

\index{Cymmer , Rhondda Cynon Taf@Cymmer, \emph{Rhondda Cynon Taf}}

Death of Eurwen Davies (Lab).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Chris Williams & Lab & 740\\
Nicole Griffiths & PC & 470\\
Paul Wasley & Ind & 142\\
Steven Rogers & C & 41\\
Kevin Jakeaway & Grn & 23\\
\end{tabular*}

\subsubsection*{Treherbert \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[14th October; Lab gain from PC]}

\index{Treherbert , Rhondda Cynon Taf@Treherbert, \emph{Rhondda Cynon Taf}}

Resignation of Percy Jones (PC).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Luke Bouchard & Lab & 883\\
Irene Pearce & PC & 855\\
\end{tabular*}

\subsection{Swansea}
\index{Swansea}

\subsubsection*{Newton \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[21st October; C gain from LD]}

\index{Newton , Swansea@Newton, \emph{Swansea}}

Resignation of Susan Waller (LD).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Miles Thomas & C & 545\\
Simon Arthur & LD & 299\\
Pam Erasmus & Lab & 187\\
Peter Birch & Ind & 108\\
Rob Lowe & PC & 31\\
\end{tabular*}

\section{Gwent}

\subsection{Blaenau Gwent}
\index{Blaenau Gwent}

\subsubsection*{Tredegar Central and West \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[8th July]}

\index{Tredegar Central and West , Blaenau Gwent@Tredegar C. \& W., \emph{Blaenau Gwent}}

Death of Derek Morris (Lab).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Bernard Willis & Lab & 797\\
Tony Gregory & Ind & 334\\
\end{tabular*}

\subsection{Caerphilly}
\index{Caerphilly}

\subsubsection*{Blackwood \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[8th July; Lab gain from Ind]}

\index{Blackwood , Caerphilly@Blackwood, \emph{Caerphilly}}

Resignation of Kevin Etheridge (Ind).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Nigel Dix & Lab & 545\\
Claire Caple & Ind & 469\\
Andrew Farina-Childs & PC & 355\\
Ian Chivers & C & 170\\
\end{tabular*}

\section{Mid and West Wales}

\subsection{Carmarthenshire}
\index{Carmarthenshire}

\subsubsection*{Cenarth \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[4th November; PC gain from Ind]}

\index{Cenarth , Carmarthenshire@Cenarth, \emph{Carmarthenshire}}

Death of Haydn Jones (Ind).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Hazel Evans & PC & 638\\
Henrietta Hensher & C & 141\\
\end{tabular*}

\subsection{Ceredigion}
\index{Ceredigion}

\subsubsection*{Ciliau Aeron \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[Tuesday 30th November]}

\index{Ciliau Aeron , Ceredigion@Ciliau Aeron, \emph{Ceredigion}}

Disqualification of Moelfryn Maskell (PC) by the Adjudication Panel for Wales.

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
John Lumley & PC & 367\\
Sonia Williams & LD & 247\\
Luke Evetts & C & 43\\
\end{tabular*}

\section{North Wales}

\subsection{Conwy}
\index{Conwy}

\subsubsection*{Mostyn \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[24th June]}

\index{Mostyn , Conwy@Mostyn, \emph{Conwy}}

Death of Alun Barrett (Lab).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Jobi Hold & Lab & 348\\
Gary Burchett & C & 310\\
Janet Jones & Ind & 198\\
\end{tabular*}

\subsubsection*{Eglwysbach \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[18th November]}

\index{Eglwysbach , Conwy@Eglwysbach, \emph{Conwy}}

Resignation of Angharad Booth-Taylor (PC).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Michael Rayner & PC & 386\\
David Williams & C & 145\\
\end{tabular*}

%\subsubsection*{Marl \hspace*{\fill}\nolinebreak[1]%
%\enspace\hspace*{\fill}
%\finalhyphendemerits=0
%[tba]}
%
%\index{Marl , Conwy@Marl, Conwy}
%
%Resignation of Linda Hurr (C).
%
%\noindent
%\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
%?
%\end{tabular*}

\subsection{Gwynedd}
\index{Gwynedd}

LlG = Llais Gwynedd

\subsubsection*{Diffwys and Maenofferen \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[15th July]}

\index{Diffwys and Maenofferen , Gwynedd@Diffwys \& Maenofferen, \emph{Gwynedd}}

Resignation of Gwilym Roberts (LlG).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Richard Jones & LlG & 185\\
Paul Thomas & PC & 181\\
\end{tabular*}

\subsubsection*{Bowydd and Rhiw \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[30th September; PC gain from LlG]}

\index{Bowydd and Rhiw , Gwynedd@Bowydd \& Rhiw, \emph{Gwynedd}}

Resignation of Dafydd Hughes (LlG).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Paul Thomas & PC & 338\\
Donna Morgan & LlG & 246\\
\end{tabular*}

\subsubsection*{Seiont \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[7th October; LlG gain from Ind]}

\index{Seiont , Gwynedd@Seiont, \emph{Gwynedd}}

Death of Bob Anderson (Ind).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
James Cooke & LlG & 399\\
Menna Thomas & PC & 279\\
Tecwyn Thomas & Lab & 184\\
Gareth Edwards & Ind & 91\\
Llinos Thomas & C & 23\\
\end{tabular*}

\subsection{Isle of Anglesey}
\index{Isle of Anglesey}

\subsubsection*{Rhosneigr \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[18th November]}

\index{Rhosneigr , Isle of Anglesey@Rhosneigr, \emph{Isle of Anglesey}}

Resignation of Phil Fowlie (Ind).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Richard Dew & Ind & 319\\
Martin Peet & C & 58\\
\end{tabular*}

\section{Clyde Councils}

\subsection{Glasgow}
\index{Glasgow}

\subsubsection*{Drumchapel/Anniesland \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Drumchapel/Anniesland , Glasgow@Drumchapel/\hspace{0pt}Anniesland, \emph{Glasgow}}

Resignation of Steven Purcell (Lab).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
Christopher Hughes & Lab & 5710\\
Frank Rankin & SNP & 2197\\
Paul McGarry & LD & 1143\\
Richard Sullivan & C & 710\\
Eileen Duke & Grn & 375\\
\end{tabular*}

\columnbreak

\subsection{South Lanarkshire}
\index{South Lanarkshire}

EKA = East Kilbride Alliance

\subsubsection*{East Kilbride West \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[28th October]}

\index{East Kilbride West , South Lanarkshire@East Kilbride W., \emph{S. Lanarks.}}

Resignation of Michael McCann MP (Lab).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
\emph{First preferences}\\
Alan Scott & Lab & 847\\
Pat McGuire & SNP & 571\\
Ian Harrow & C & 403\\
Raymond Burke & Grn & 82\\
Brian Jones & EKA & 71\\
Gordon Smith & LD & 70\\
\end{tabular*}

\emph{Exclude Burke, Jones and Smith}: Scott 892 McGuire 641 Harrow 455

%\noindent
%\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
%\multicolumn{3}{@{\extracolsep{\fill}}l}{\emph{Exclude Burke, Jones and Smith}}\\
%Alan Scott & Lab & 892\\
%Pat McGuire & SNP & 641\\
%Ian Harrow & C & 455\\
%\end{tabular*}

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
\emph{Exclude Harrow}\\
Alan Scott & Lab & 973\\
Pat McGuire & SNP & 761\\
\end{tabular*}

\section{Forth Councils}

\subsection{Edinburgh}
\index{Edinburgh}

Pirate = Pirate Party Scotland

\subsubsection*{Liberton/Gilmerton \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[9th September]}

\index{Liberton/Gilmerton , Edinburgh@Liberton\slash Gilmerton, \emph{Edinburgh}}

Resignation of Ian Murray (Lab).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
\emph{First preferences}\\
Bill Cook & Lab & 2974\\
Richard Lewis & SNP & 1382\\
Stephanie Murray & C & 1020\\
John Knox & LD & 722\\
Peter McColl & Grn & 201\\
Colin Fox & SSP & 169\\
Mev Brown & Ind & 128\\
Philip Hunt & Pirate & 43\\
\end{tabular*}

\emph{Exclude Brown, Fox, Hunt and McColl}: Cook 3121 Lewis 1484 Murray 1055 Knox 816

%\noindent
%\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
%\multicolumn{3}{@{\extracolsep{\fill}}l}{\emph{Exclude Brown, Fox, Hunt and McColl}}\\
%Bill Cook & Lab & 3121\\
%Richard Lewis & SNP & 1494\\
%Stephanie Murray & C & 1055\\
%John Knox & LD & 816\\
%\end{tabular*}

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
\emph{Exclude Knox}\\
Bill Cook & Lab & 3308\\
Richard Lewis & SNP & 1698\\
Stephanie Murray & C & 1262\\
\end{tabular*}

\columnbreak

\section{Highland Councils}

\subsection{Moray}
\index{Moray}

SSCUP = Scottish Senior Citizens Unity Party

\subsubsection*{Forres \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[11th November; Ind gain from C]}

\index{Forres , Moray@Forres, \emph{Moray}}

Resignation of Iain Young (C).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
\emph{First preferences}\\
Aaron McLean & SNP & 773\\
Lorna Creswell & Ind & 562\\
Paul McBain & C & 463\\
Anne Skene & Ind & 463\\
Fabio Villani & Grn & 401\\
Mark Cascarino & Lab & 195\\
Janet Kennedy & Ind & 192\\
Andy Anderson & SSCUP & 132\\
Jane Cotton & Ind & 30\\
\end{tabular*}

\emph{Exclude Anderson and Cotton}: McLean 789 Creswell 615 Skene 491 McBain 476 Villani 405 Cascarino 201 Kennedy 201

%\noindent
%\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
%\multicolumn{3}{@{\extracolsep{\fill}}l}{\emph{Exclude Anderson and Cotton}}\\
%Aaron McLean & SNP & 789\\
%Lorna Creswell & Ind & 615\\
%Anne Skene & Ind & 491\\
%Paul McBain & C & 476\\
%Fabio Villani & Grn & 405\\
%Mark Cascarino & Lab & 201\\
%Janet Kennedy & Ind & 201\\
%\end{tabular*}

\sloppyword{\emph{Exclude Cascarino and Kennedy}: McLean 837 Creswell 726 Skene 572 McBain 491 Villani 459}

%\noindent
%\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
%\multicolumn{3}{@{\extracolsep{\fill}}l}{\emph{Exclude Cascarino and Kennedy}}\\
%Aaron McLean & SNP & 837\\
%Lorna Creswell & Ind & 726\\
%Anne Skene & Ind & 572\\
%Paul McBain & C & 491\\
%Fabio Villani & Grn & 459\\
%\end{tabular*}

\emph{Exclude Villani}: McLean 899 Creswell 878 Skene 695 McBain 511

%\noindent
%\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
%\emph{Exclude Villani}\\
%Aaron McLean & SNP & 899\\
%Lorna Creswell & Ind & 878\\
%Anne Skene & Ind & 695\\
%Paul McBain & C & 511\\
%\end{tabular*}

\emph{Exclude McBain}: Creswell 999 McLean 950 Skene 860

%\noindent
%\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
%\emph{Exclude McBain}\\
%Lorna Creswell & Ind & 999\\
%Aaron McLean & SNP & 950\\
%Anne Skene & Ind & 860\\
%\end{tabular*}

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
\emph{Exclude Skene}\\
Lorna Creswell & Ind & 1399\\
Aaron McLean & SNP & 1045\\
\end{tabular*}

\section*{}

\section*{}

\section*{}

\columnbreak

\section{Tay Councils}

\subsection{Perth and Kinross}
\index{Perth and Kinross}

\subsubsection*{Strathallan \hspace*{\fill}\nolinebreak[1]%
\enspace\hspace*{\fill}
\finalhyphendemerits=0
[6th May]}

\index{Strathallan , Perth and Kinross@Strathallan, \emph{Perth \& Kinross}}

Death of John Law (SNP).

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
\emph{First preferences}\\
John Blackie & C & 1713\\
Tom Gray & SNP & 1555\\
Neil Gaunt & LD & 1042\\
Alistair Munro & Lab & 754\\
Chris Rennie & Ind & 61\\
\end{tabular*}

\emph{Exclude Munro and Rennie}: Blackie 1785 Gray 1769 Gaunt 1321

%\noindent
%\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
%\emph{Exclude Munro and Rennie}\\
%John Blackie & C & 1785\\
%Tom Gray & SNP & 1769\\
%Neil Gaunt & LD & 1321\\
%\end{tabular*}

\noindent
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} p{0.545\columnwidth} >{\itshape}l r @{\extracolsep{\fill}}}
\emph{Exclude Gaunt}\\
Tom Gray & SNP & 2299\\
John Blackie & C & 2208\\
\end{tabular*}

\end{resultsiii}
